### 2016-07-11 paper/paper.tex
added paper format

\documentclass[twoside,11pt]{article}

% Any additional packages needed should be included after jmlr2e.
% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

\usepackage{jmlr2e}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

% Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}

%\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{Marina Meil\u{a} and Michael I. Jordan}

% Short headings should be running head and authors last names

%\ShortHeadings{Ensemble Methods for Robust Feature Selection}{Meil\u{a} and Jordan}
\firstpageno{1}

\begin{document}

\title{Ensemble Methods for Robust Feature Selection}

\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
       \addr Department of Statistics\\
       University of Washington\\
       Seattle, WA 98195-4322, USA
       \AND
       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
       \addr Division of Computer Science and Department of Statistics\\
       University of California\\
       Berkeley, CA 94720-1776, USA}

\editor{Leslie Pack Kaelbling}

\maketitle

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
  Abstract
\end{abstract}

\begin{keywords}
  Ensemble Methods, Robust, 
\end{keywords}

\section{Motivation}

Features selection methods is a key method to work with high dimensional data.
It is widely used in areas working with high dimensional data like bioinformatics.
In the past different feature selection methods have been presented.
Additionally, ensemble methods have been presented by \cite{saeys2008}

% Acknowledgements should go at the end, before appendices and references

%\acks{I want to thank my mum}

% Manual newpage inserted to improve layout of sample file - not
% needed in general before appendices/bibliography.

\newpage

\appendix
%\section*{Appendix A.}
%\label{app:some appendix}

% Note: in this sample, the section number is hard-coded in. Following
% proper LaTeX conventions, it should properly be coded as a reference:

\vskip 0.2in
\bibliography{references}

\end{document}

### 2016-07-11 benchmarks.py
RawDataSet Experiment FeatureSelector and FeatureSelection were merged FeatureSelector and EnsembleMethod implements DataSetFeatureSelector

@@ -5,24 +5,34 @@ import multiprocessing
 import ctypes
 from feature_selector import FeatureSelector
 from robustness_measure import Measure, JaccardIndex
-from feature_selection import FeatureSelectionGenerator
+from sklearn.metrics import f1_score
+from collections import Iterable
 
 
 class Benchmark(metaclass=ABCMeta):
     feature_selector = None
 
     def generate_features_selection(self, data, labels):
-        if self.feature_selector is None:
+        if not isinstance(self.feature_selector, FeatureSelector):
             raise TypeError("feature_selector needs to be defined")
-        generator = FeatureSelectionGenerator(self.feature_selector)
-        return generator.generate(data, labels, self.cv(labels.shape[0]), "rank")
+
+        return self.feature_selector.generate(data, labels, self.cv(labels.shape[0]), "rank")
 
     @staticmethod
     def cv(sample_size):
         pass
 
+    # Returns mean results for each measure
+    def run(self, *args, **kwargs):
+        mean_results = []
+        for i, measure_results in enumerate(self.run_raw_result(*args, **kwargs)):
+            mean_results.append(np.mean(measure_results))
+
+        return np.array(mean_results)
+
     @abstractmethod
-    def run(self, data, labels, features_selection=None):
+    # Returns an Iterable, one item per measures with all the results associated with it
+    def run_raw_result(self, data, labels, features_selection=None) -> Iterable:
         pass
 
     @abstractmethod
@@ -43,14 +53,13 @@ class MeasureBenchmark(Benchmark):
 
         self.measures = measure
 
-    def run(self, data, labels, features_selection=None):
+    def run_raw_result(self, data, labels, features_selection=None):
         if features_selection is None:
             features_selection = self.generate_features_selection(data, labels)
 
         features_selection = np.array(features_selection).T
-        shared_array_base = multiprocessing.Array(ctypes.c_double, len(self.measures))
-        shared_measures_array = np.ctypeslib.as_array(shared_array_base.get_obj())
-        shared_measures_array = shared_measures_array.reshape(len(self.measures))
+
+        measures_results = multiprocessing.Manager().dict()
 
         processes = []
         for i in range(len(self.measures)):
@@ -58,7 +67,7 @@ class MeasureBenchmark(Benchmark):
                 target=self.measures[i].run_and_set_in_results,
                 kwargs={
                     'features_selection': features_selection,
-                    'results': shared_measures_array,
[…]

### 2016-07-11 experiments.py

@@ -1,5 +1,5 @@
 from benchmarks import MeasureBenchmark, AccuracyBenchmark, Benchmark, FMeasureBenchmark
-from ensemble_methods import FeatureSelection
+from feature_selector import DataSetFeatureSelector
 from tabulate import tabulate
 import numpy as np
 import csv
@@ -107,88 +107,93 @@ class AccuracyExperiment(Experiment):
         super().print_results()
 
 
-class DataSetExperiments:
-    def __init__(self, feature_selectors, measures, classifiers, working_dir=".."):
-        self.measure_experiment = MeasureExperiment(feature_selectors, measures)
-        self.accuracy_experiment = AccuracyExperiment(feature_selectors, classifiers)
-        self.results_folder = working_dir
-
-    def run_data_set(self, name, file_name="output.csv"):
-        data, labels = DataSets.load(name)
-
-        self.measure_experiment.run(data, labels)
-        self.measure_experiment.print_results()
-        self.measure_experiment.save_results(file_name)
-
-        self.accuracy_experiment.run(data, labels)
-        self.accuracy_experiment.print_results()
-        self.accuracy_experiment.save_results(file_name)
-
-
-class EnsembleMethodExperiment(Experiment):
-    def __init__(self, ensemble_methods, benchmark: Benchmark, feature_selectors=None):
-        if not isinstance(ensemble_methods, list):
-            ensemble_methods = [ensemble_methods]
-
-        self.ensemble_methods = ensemble_methods
+class DataSetExperiment(Experiment):
+    def __init__(self, benchmark: Benchmark, data_set_feature_selectors):
         self.benchmark = benchmark
-        self.feature_selectors = [] if feature_selectors is None else [FeatureSelection(f) for f in feature_selectors]
-        self.results = np.zeros((len(benchmark.get_measures()), len(ensemble_methods) + len(self.feature_selectors)))
+
+        if not isinstance(data_set_feature_selectors, list):
+            data_set_feature_selectors = [data_set_feature_selectors]
+
+        for data_set_feature_selector in data_set_feature_selectors:
+            if not isinstance(data_set_feature_selector, DataSetFeatureSelector):
+                raise ValueError("Only DataSetFeatureSelector can be used")
+
+        self.feature_selectors = data_set_feature_selectors
+
+        self.results = np.zeros((len(benchmark.get_measures()), len(self.feature_selectors)))
 
[…]

### 2016-07-11 feature_selector.py

@@ -12,15 +12,50 @@ from sklearn.grid_search import GridSearchCV
 from sklearn.feature_selection import RFE
 # Lasso
 from sklearn.linear_model import LassoCV
+from data_sets import DataSets, PreComputedData
+import multiprocessing
+import os
+import errno
 
 
-class FeatureSelector(metaclass=ABCMeta):
+class DataSetFeatureSelector(metaclass=ABCMeta):
+    @staticmethod
+    def check_data_set_and_cv(data_set, cv_generator):
+        if not callable(cv_generator):
+            raise ValueError("cv_generator should be callable")
+        if data_set not in DataSets.data_sets:
+            raise ValueError("No data set found with the name {}".format(data_set))
+
+    @abstractmethod
+    def rank_data_set(self, data_set, cv_generator):
+        self.check_data_set_and_cv(data_set, cv_generator)
+
+    @abstractmethod
+    def weight_data_set(self, data_set, cv_generator):
+        self.check_data_set_and_cv(data_set, cv_generator)
+
+    @staticmethod
+    def normalize(vector):
+        return preprocessing.MinMaxScaler().fit_transform(vector)
+
+    @staticmethod
+    def rank_weights(features_weight):
+        features_rank = scipy.stats.rankdata(features_weight, method='ordinal')
+
+        # shuffle same features
+        for unique_value in np.unique(features_weight):
+            unique_value_args = np.argwhere(features_weight == unique_value).reshape(-1)
+            unique_value_args_shuffled = np.random.permutation(unique_value_args)
+            features_rank[unique_value_args] = features_rank[unique_value_args_shuffled]
+
+        return features_rank
+
+
+class FeatureSelector(DataSetFeatureSelector, metaclass=ABCMeta):
+    max_parallelism = multiprocessing.cpu_count()
+
     def __init__(self):
         self.__name__ = type(self).__name__
-
-    def run_and_set_in_results(self, data, labels, results, result_index, method):
-        np.random.seed()
-        results[result_index] = getattr(self, method)(data, labels)
 
     # Each column is an observation, each row a feature
     def rank(self, data, labels):
@@ -31,20 +66,87 @@ class FeatureSelector(metaclass=ABCMeta):
     def weight(self, data, labels):
         pass
 
-    @staticmethod
-    def normalize(vector):
-        return preprocessing.MinMaxScaler().fit_transform(vector)
+    def generate(self, data, labels, cv, method):
[…]

### 2016-07-11 goodness_measure.py

@@ -39,7 +39,7 @@ class GoodnessMeasure(Measure, metaclass=ABCMeta):
         else:
             self.n_significant_features = np.sum([feature_probe_labels == 1])
 
-    def measure(self, features_ranks):
+    def measures(self, features_ranks):
         if not self.n_significant_features:
             return 0
 
@@ -48,7 +48,7 @@ class GoodnessMeasure(Measure, metaclass=ABCMeta):
             goodness.append(self.goodness(
                 RankData(features_ranks[:, i].T, self.n_significant_features)
             ))
-        return np.mean(goodness)
+        return goodness
 
     @abstractmethod
     def goodness(self, data: RankData):

### 2016-07-11 robustness_measure.py

@@ -9,47 +9,48 @@ class Measure(metaclass=ABCMeta):
 
     def run_and_set_in_results(self, features_selection, results, result_index):
         np.random.seed()
-        results[result_index] = self.measure(features_selection)
+        results[result_index] = self.measures(features_selection)
 
     @abstractmethod
     # features ranks is matrix with each rows represent a feature, and the columns its rankings
-    def measure(self, features_ranks):
+    def measures(self, features_ranks):
         pass
 
 
-class Dummy(Measure):
-    def measure(self, features_ranks):
+class RobustnessMeasure(Measure, metaclass=ABCMeta):
+    def measures(self, features_ranks):
+        robustness = []
+        for i in range(1, features_ranks.shape[1]):
+            for j in range(i):
+                robustness.append(self.robustness(features_ranks[:, i], features_ranks[:, j]))
+        return robustness
+
+    @abstractmethod
+    def robustness(self, ranks1, ranks2):
+        pass
+
+
+class Dummy(RobustnessMeasure):
+    def robustness(self, ranks1, ranks2):
         return 1
 
 
-def mean_of_lower_triangular(matrix):
-    lower_triangular_index = np.tril_indices(matrix.shape[0], -1)
-    return np.mean(matrix[lower_triangular_index])
-
-
-class Spearman(Measure):
-
+class Spearman(RobustnessMeasure):
     def __init__(self):
         super().__init__()
         self.__name__ = "Spearman Coefficient"
 
-    def measure(self, features_ranks):
-        spearman_correlation_matrix, _ = scipy.stats.spearmanr(features_ranks)
-        return mean_of_lower_triangular(spearman_correlation_matrix)
+    def robustness(self, ranks1, ranks2):
+        return scipy.stats.spearmanr(ranks1, ranks2)[0]
 
 
 class JaccardIndex(Measure):
-
     def __init__(self, percentage=0.1):
         super().__init__()
         self.percentage = percentage
         self.__name__ = "Jaccard Index {:.2%}".format(percentage)
 
-    def measure(self, features_ranks):
-        indices = self.matrix(features_ranks)
-        return mean_of_lower_triangular(indices)
-
-    def matrix(self, features_ranks):
+    def measures(self, features_ranks):
         if np.any(np.min(features_ranks, axis=0) != np.ones(features_ranks.shape[1], dtype=np.int)):
             print(features_ranks)
[…]

### 2016-07-11 test.py

@@ -52,22 +52,24 @@ DataSets.save_artificial(
     )
 )
 
-# e = []
+e_methods = [
+    ensemble_methods.Mean(em_feature_selectors)
+]
 # for i in range(1, 10):
 #     for j in range(1, 10):
 #         for k in range(1, 10):
-#             e.append(ensemble_methods.SMean(feature_selectors, min_mean_max=[i, j, k]))
+#             e_methods.append(ensemble_methods.SMean(feature_selectors, min_mean_max=[i, j, k]))
 
 
-e_methods = [
-    ensemble_methods.Mean(em_feature_selectors),
-    ensemble_methods.SMean(em_feature_selectors, min_mean_max=[9, 3, 1]),
-    ensemble_methods.SMeanWithClassifier(
-        em_feature_selectors,
-        classifiers,
-        min_mean_max=[9, 3, 1]
-    ),
-]
+# e_methods = [
+#     ensemble_methods.Mean(em_feature_selectors),
+#     ensemble_methods.SMean(em_feature_selectors, min_mean_max=[9, 3, 1]),
+#     ensemble_methods.SMeanWithClassifier(
+#         em_feature_selectors,
+#         classifiers,
+#         min_mean_max=[9, 3, 1]
+#     ),
+# ]
 
 # exp = EnsembleFMeasureExperiment(
 #     classifiers,
@@ -82,31 +84,28 @@ e_methods = [
 
 robustnessf_exp = EnsembleFMeasureExperiment(
     classifiers,
-    e_methods,
-    feature_selectors=feature_selectors
+    feature_selectors + e_methods,
 )
 
 
-accuracy_exp = EnsembleMethodExperiment(
-    e_methods,
+accuracy_exp = DataSetExperiment(
     AccuracyBenchmark(classifiers, percentage_of_features=.01),
-    feature_selectors
+    feature_selectors + e_methods
 )
 
 
 def do_complete_analysis(data_set, append_results=False):
-    print(data_set)
+    print(data_set.upper())
     measures = [
         robustness_measure.Spearman(),
         robustness_measure.JaccardIndex(percentage=0.01),
         robustness_measure.JaccardIndex(percentage=0.05),
-        goodness_measure.Precision(data_set),
-        goodness_measure.XPrecision(data_set)
+        # goodness_measure.Precision(data_set),
+        # goodness_measure.XPrecision(data_set)
     ]
-    robustness_exp = EnsembleMethodExperiment(
-        e_methods,
[…]

### 2016-07-11 test/test_feature_selectors.py

@@ -11,31 +11,10 @@ class TestFeatureSelector:
         assert expected_result.tolist() == FeatureSelector.normalize(a).tolist()
 
     def test_rank_weights(self):
-        weights = np.arange(5) / 4
-        expected_results = np.arange(5) + 1
+        weights = np.array([0.5, 0.1, 0.5, 0.6])
+        ranked_weights = FeatureSelector.rank_weights(weights).tolist()
 
-        assert expected_results.tolist() == FeatureSelector.rank_weights(weights).tolist()
-
-    def test_rank_weights(self):
-        weights = np.arange(5) / 4
-        expected_results = np.arange(5) + 1
-
-        assert expected_results.tolist() == FeatureSelector.rank_weights(weights).tolist()
-
-    def test_rank_weights(self):
-        weights = np.array([0.5,0.1,0.5,0.6])
-        assert np.any([3., 1., 2., 4.] == FeatureSelector.rank_weights(weights).tolist(),
-                      [2., 1., 3., 4.] == FeatureSelector.rank_weights(weights).tolist())
-
-
-class TestDummy:
-    features_weight = [0.5, 1.0, 0.5, 0.7, 0.7]
-
-    def test_rank_weights(self):
-        dummy = Dummy()
-        features_rank = dummy.rank_weights(self.features_weight)
-        print(features_rank)
-        assert np.allclose([1, 5, 2, 3, 4], dummy.rank_weights(self.features_weight))
+        assert [3., 1., 2., 4.] == ranked_weights or [2., 1., 3., 4.] == ranked_weights
 
 
 class TestSymmetricalUncertainty:

### 2016-07-12 paper/paper.tex
added poster

@@
 
-\section{Motivation}
+\section{Introduction}
 
-Features selection methods is a key method to work with high dimensional data.
-It is widely used in areas working with high dimensional data like bioinformatics.
-In the past different feature selection methods have been presented.
-Additionally, ensemble methods have been presented by \cite{saeys2008}
+Feature selection is a preprocessing step used in machine learning application to find
+a small subset of features in order to build a more accurate, simpler and faster model.
+Moreover it allows domain experts to gain a better understanding of the data, by focusing
+ on the selected subset.However in domains such as biomedical applications, 
+where subsequent analysis are costly, not only the model performance but also the robustness
+ of the feature selection method is important. Domain experts would prefer a more stable
+ algorithm to have more confidence in the selected features. One approach for more robust
+ results are ensemble methods.
 
+In ensemble learning multiple algorithms are combined to obtain better performance or stability.
+We build on the work of \cite{saeys2008} who applied ensemble learning by using
+the same feature selector on different subsets. In this work we investigate the effect of ensemble methods
+further by using multiple feature selection methods. In order to find a good trade-off between robustness
+and model performance, multiple feature selection methods were combined in different ways.
+
+\section{Method}
+A entropy based measurement. It measures the influence of the class on a feature entropy-wise and normalizes it
+
+We first calculate the weights if avaible by the features selector otherwise the ranks.
+For feature selector, which do not omit normalized weights between a0 and 1, we normalize
+the weights to the range $[0,1]$. We also normalize the ranks of the features selectors returning
+ranks to the range $[0,1]$. Now that we combine the weights after one of the following rules: \ldots
+
+\section{Weaknesses}
+- Do SVM\_RFE with exponential rising
+- SU achieved high values in the paper, in our results SU weighted a lot of features the 
+same; therefore for robustness same weights have to be shuffled to not accidental increase
+robustness by order of features
 % Acknowledgements should go at the end, before appendices and references

### 2016-07-13 data_sets.py
bugs

@@ -58,11 +58,11 @@ class DataSets:
             {
                 "feat_labels": "/GISETTE/GISETTE/gisette_feat.labels",
                 "path": "/GISETTE/GISETTE/gisette_valid.data",
-                "apply_transform": lambda x: np.transpose(x)[:, :400],
+                "apply_transform": lambda x: np.transpose(x)[:, :200],
             },
             {
                 "path": "/GISETTE/GISETTE/gisette_valid.labels",
-                "apply_transform": lambda x: x[:400]
+                "apply_transform": lambda x: x[:200]
             }
         ),
         "artificial": (

### 2016-07-13 ensemble_methods.py

@@ -13,7 +13,7 @@ class EnsembleMethod(DataSetFeatureSelector, metaclass=ABCMeta):
     max_parallelism = multiprocessing.cpu_count()
 
     def __init__(self, data_set_feature_selectors):
-        self.__name__ = type(self).__name__
+        super().__init__()
 
         if not isinstance(data_set_feature_selectors, list):
             data_set_feature_selectors = [data_set_feature_selectors]

### 2016-07-13 experiments.py

@@ -5,6 +5,7 @@ import numpy as np
 import csv
 from data_sets import DataSets
 import os
+import sys
 import errno
 
 
@@ -154,21 +155,50 @@ class RawDataSetExperiment:
                 raise ValueError("Only DataSetFeatureSelector can be used")
 
         self.feature_selectors = data_set_feature_selectors
+        self.results = None
+        self.data_sets = None
 
     def run(self, data_sets):
-        results = []
+        self.results = []
+        self.data_sets = data_sets
 
         for i, data_set in enumerate(data_sets):
+            print(data_set)
             data, labels = DataSets.load(data_set)
-            results.append([])
+            self.results.append([])
             for feature_selector in self.feature_selectors:
-                results[i].append(self.benchmark.run_raw_result(
+                print(feature_selector.__name__)
+                self.results[i].append(self.benchmark.run_raw_result(
                     data,
                     labels,
                     feature_selector.rank_data_set(data_set, self.benchmark.cv)
                 ))
+        self.results = np.array(self.results)
+        return self.results
 
-        return np.array(results)
+    def save_results(self, filename=None):
+        if filename is None:
+            filename = type(self.benchmark).__name__
+
+        root_dir = DataSets.root_dir + "/results/RAW"
+
+        try:
+            os.makedirs(root_dir)
+        except OSError as exception:
+            if exception.errno != errno.EEXIST:
+                raise
+
+        def write(dim, data):
+            with open("{}/{}_{}.txt".format(root_dir, filename, dim), "w") as f:
+                for d in data:
+                    f.write(d + "\n")
+
+        np.save("{}/{}.npy".format(root_dir, filename), self.results)
+
+        write(0, self.data_sets)
+        write(1, [f.__name__ for f in self.feature_selectors])
+        write(2, [m.__name__ for m in self.benchmark.get_measures()])
+
 
 
 class EnsembleFMeasureExperiment(Experiment):
@@ -195,10 +225,14 @@ class EnsembleFMeasureExperiment(Experiment):
             beta=self.beta,
         )
 
+        len_fs = len(self.feature_selectors)
+        size = len(data_sets) * len_fs
+
         for i, data_set in enumerate(data_sets):
             data, labels = DataSets.load(data_set)
 
             for j, feature_selector in enumerate(self.feature_selectors):
+                sys.stdout.write("\rProgress: {:.2%}".format((i * len_fs + j)/size))
                 self.results[i, j] = benchmark.run(
                     data,
                     labels,

### 2016-07-13 feature_selector.py

@@ -19,6 +19,9 @@ import errno
 
 
 class DataSetFeatureSelector(metaclass=ABCMeta):
+    def __init__(self):
+        self.__name__ = type(self).__name__
+
     @staticmethod
     def check_data_set_and_cv(data_set, cv_generator):
         if not callable(cv_generator):
@@ -53,9 +56,6 @@ class DataSetFeatureSelector(metaclass=ABCMeta):
 
 class FeatureSelector(DataSetFeatureSelector, metaclass=ABCMeta):
     max_parallelism = multiprocessing.cpu_count()
-
-    def __init__(self):
-        self.__name__ = type(self).__name__
 
     # Each column is an observation, each row a feature
     def rank(self, data, labels):

### 2016-07-13 test.py

@@ -8,23 +8,48 @@ from sklearn.neighbors import KNeighborsClassifier
 from sklearn.svm import SVC
 from sklearn.ensemble import RandomForestClassifier
 from artificial_data_sets2 import ArtificialData, ArtificialLabels
+from sklearn.grid_search import GridSearchCV
 
-em_feature_selectors = [
+feature_selectors = [
     SymmetricalUncertainty(),
     Relief(),
     SVM_RFE(),
     LassoFeatureSelector(),
 ]
 
-feature_selectors = em_feature_selectors + [
-    Random()
-]
+
+class SVC_Grid:
+    def __init__(self, *args, **kwargs):
+        self.args = args
+        self.kwargs = kwargs
+        self.classifier = None
+
+    def fit(self, data, labels):
+        grid_search = GridSearchCV(
+            SVC(),
+            {
+                "C": [1, 10, 100, 1000]
+            },
+            cv=5,
+            scoring='precision'
+        )
+        grid_search.fit(data, labels)
+        self.kwargs["C"] = grid_search.best_params_["C"]
+
+        self.classifier = SVC(*self.args, **self.kwargs)
+
+        self.classifier.fit(data, labels)
+
+    def predict(self, data):
+        return self.classifier.predict(data)
+
+    def score(self, data, labels):
+        return self.classifier.score(data, labels)
+
 
 classifiers = [
     KNeighborsClassifier(3),
-    SVC(kernel="linear", C=0.025),
-    SVC(kernel="poly", degree=3, gamma=0, coef0=2, C=0.1),
-    SVC(kernel="poly", degree=1, gamma=0, coef0=1, C=0.5),
+    SVC_Grid(kernel="linear"),
     RandomForestClassifier(max_depth=5, n_estimators=10, max_features=1)
 ]
 
@@ -32,40 +57,40 @@ import warnings
 
 warnings.filterwarnings('ignore')
 
-total_features = 1e4
-n_significant_features = int(total_features*0.01)
-DataSets.save_artificial(
-    *ArtificialData.generate(
-        n_samples=300,
-        n_features=total_features,
-        n_significant_features=n_significant_features,
-        feature_distribution=ArtificialData.multivariate_normal(
-            mean=np.zeros(n_significant_features),
-            cov=ArtificialData.uniform(-2, 2)
-        ),
[…]

### 2016-07-13 paper/paper.tex
paper fs SU, RELIEF, SVM_RFE added

@@
 \usepackage{jmlr2e}
+\usepackage{amsmath}
 
@@
 the same feature selector on different subsets. In this work we investigate the effect of ensemble methods
-further by using multiple feature selection methods. In order to find a good trade-off between robustness
-and model performance, multiple feature selection methods were combined in different ways.
+further by using multiple feature selection methods. 
+In order to find a good trade-off between robustness and model performance, multiple feature selection methods were
+combined in multiple ways.
 
-\section{Method}
-A entropy based measurement. It measures the influence of the class on a feature entropy-wise and normalizes it
+\section{Feature selection methods}
 
+Symmetrical Uncertainty \citep{press1996numerical} is entropy based measurement. It is the normalized mutual information between the feature
+and the class. The mutual information measures the influence of the knowledge of the class on the feature value
+in terms of entropy and normalizes it. More details about mutual information can be found in \cite{paninski2003estimation}.
+\begin{equation}
+  \label{eq:su}
+  SU(F,C) = 2 \frac{H(F) - H(F|C)}{H(F) + H(C)} \textrm{, where } H(\cdot) \textrm{ is the entropy.}
+\end{equation}
+
+The second feature selection method we used is RELIEF \citep{kira1992feature}. In the beginning the weights are initialize
+with a $0$ weight.
+It then iteratively takes a random sample $x_i$ and compares it to their nearest neighboring sample belonging to their class
+$\textrm{Near-hit}_i$ and the opposite one $\textrm{Near-miss}_i$ in terms of a similarity measurement.
+The weights are set by how well these two similarity measurements distinguish as it can be seen in equation \ref{eq:relief}.
+In the standard case of RELIEF for comparisment the euclidean distance is used for numerical values. This inherits the
+assumption that features which are nearer to each other are also more similar, which should not be correct in each application
+area.
+\begin{equation}
+  \label{eq:relief}
+  W_i = W_i - \|x_i - \textrm{Near-hit}_i\|_2^2 + \|x_i - \textrm{Near-miss}_i\|_2^2
+\end{equation}
+
+The third feature selection method we used was a recursive feature elmination in combination with SVM \citep{guyon2002gene}.
+Recursive feature elimination fits a SVM and ranks the feature according to their importance in the model,
+based on the weight vector of the hyperplane.
+More precisely after obtaining the solution for the primal problem of the SVM in equation \ref{eq:svm_primal},
+the ranking coefficients $c_i$ for the features are then calculated by squaring the weights $c_i = w_i^2$.
+\begin{alignat}{-1}
+     \min_{w,b}  & \quad \frac12\|w\|^2 + C\sum_{i=1}^m \xi_i & & & \label{eq:svm_primal} \\ 
+   \text{s.\,t.} & \quad y^{(i)} (w^Tx^{i} + b) & \quad \geq & \quad 1 -\xi_i &&
+                   \quad \forall \, i = 1, \ldots, m \nonumber \\
+                 & \quad \xi_i                  & \quad \geq & \quad 0 &&
+                   \quad \forall \, i = 1, \ldots, m \nonumber 
+\end{alignat}
+
+The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left.
+In our case we discarded each step $10\%$ of the size of all features of the features being left. This means that
+in each step we discarded the same amount of features. This procedure was repeated until a subset of the size
+of $1\%$ of all features was left.
+
+\section{Ensemble methods}
+%Weighting
 We first calculate the weights if avaible by the features selector otherwise the ranks.
@@
 
-\section{Weaknesses}
+Ensemble method: The weights of different feature selection methods are first computed and then linearly aggregated to obtain the new weights. Three methods were used:
+The mean is used as the new weight.
+The minimum, maximum and the mean are linearly aggregated.
+The accuracy is estimated for each of the feature selector for multiple classifiers.
+Then the different feature weights are accordingly weighted to favor the feature selector with the best performance and the previous method is applied.
+
+\section{Results}
 - Do SVM\_RFE with exponential rising
@@
 robustness by order of features
+- The noise features of the NIPS 2003 challenge data sets are highly correlated with the
+real feature; therefore no improvement has been made with feature selection in terms of 
+accuracy
 % Acknowledgements should go at the end, before appendices and references

### 2016-07-13 feature_selector.py

@@ -205,7 +205,8 @@ class SVM_RFE(ClassifierFeatureSelector):
                 C=self.find_best_hyper_parameter_SVC(data, labels)
             ),
             n_features_to_select=round(len(data) * 0.01),
-            step=self.step
+            step=self.step,
+            stepwise_selection=True
         )
         rfe.fit(data.T, labels)
         ordered_ranks = self.reverse_order(rfe.ranking_)

### 2016-07-13 sklearn/feature_selection/rfe.py
stepwise selection adde to RFE methods

@@ -1,0 +1,465 @@
+# Authors: Alexandre Gramfort <alexandre.gramfort@inria.fr>
+#          Vincent Michel <vincent.michel@inria.fr>
+#          Gilles Louppe <g.louppe@gmail.com>
+#
+# License: BSD 3 clause
+
+"""Recursive feature elimination for feature ranking"""
+
+import warnings
+import numpy as np
+from ..utils import check_X_y, safe_sqr
+from ..utils.metaestimators import if_delegate_has_method
+from ..base import BaseEstimator
+from ..base import MetaEstimatorMixin
+from ..base import clone
+from ..base import is_classifier
+from ..cross_validation import check_cv
+from ..cross_validation import _safe_split, _score
+from ..metrics.scorer import check_scoring
+from .base import SelectorMixin
+
+
+class RFE(BaseEstimator, MetaEstimatorMixin, SelectorMixin):
+    """Feature ranking with recursive feature elimination.
+
+    Given an external estimator that assigns weights to features (e.g., the
+    coefficients of a linear model), the goal of recursive feature elimination
+    (RFE) is to select features by recursively considering smaller and smaller
+    sets of features. First, the estimator is trained on the initial set of
+    features and weights are assigned to each one of them. Then, features whose
+    absolute weights are the smallest are pruned from the current set features.
+    That procedure is recursively repeated on the pruned set until the desired
+    number of features to select is eventually reached.
+
+    Read more in the :ref:`User Guide <rfe>`.
+
+    Parameters
+    ----------
+    estimator : object
+        A supervised learning estimator with a `fit` method that updates a
+        `coef_` attribute that holds the fitted parameters. Important features
+        must correspond to high absolute values in the `coef_` array.
+
+        For instance, this is the case for most supervised learning
+        algorithms such as Support Vector Classifiers and Generalized
+        Linear Models from the `svm` and `linear_model` modules.
+
+    n_features_to_select : int or None (default=None)
+        The number of features to select. If `None`, half of the features
+        are selected.
+
+    step : int or float, optional (default=1)
+        If greater than or equal to 1, then `step` corresponds to the (integer)
+        number of features to remove at each iteration.
+        If within (0.0, 1.0), then `step` corresponds to the percentage
+        (rounded down) of features to remove at each iteration.
+
+    estimator_params : dict
+        Parameters for the external estimator.
+        This attribute is deprecated as of version 0.16 and will be removed in
[…]

### 2016-07-13 feature_selector.py
rfe separated from sklearn

@@ -1,7 +1,9 @@
 from abc import ABCMeta, abstractmethod
-from sklearn import preprocessing
+
 import numpy as np
 import scipy.stats
+
+from sklearn import preprocessing
 # SU
 import skfeature.utility.mutual_information
 # Relief
@@ -9,7 +11,7 @@ import skfeature.function.similarity_based.reliefF
 # SVM_RFE
 from sklearn.svm import SVC
 from sklearn.grid_search import GridSearchCV
-from sklearn.feature_selection import RFE
+from sklearn_rfe import RFE
 # Lasso
 from sklearn.linear_model import LassoCV
 from data_sets import DataSets, PreComputedData

### 2016-07-13 sklearn_rfe.py

@@ -8,16 +8,16 @@
 
 import warnings
 import numpy as np
-from ..utils import check_X_y, safe_sqr
-from ..utils.metaestimators import if_delegate_has_method
-from ..base import BaseEstimator
-from ..base import MetaEstimatorMixin
-from ..base import clone
-from ..base import is_classifier
-from ..cross_validation import check_cv
-from ..cross_validation import _safe_split, _score
-from ..metrics.scorer import check_scoring
-from .base import SelectorMixin
+from sklearn.utils import check_X_y, safe_sqr
+from sklearn.utils.metaestimators import if_delegate_has_method
+from sklearn.base import BaseEstimator
+from sklearn.base import MetaEstimatorMixin
+from sklearn.base import clone
+from sklearn.base import is_classifier
+from sklearn.cross_validation import check_cv
+from sklearn.cross_validation import _safe_split, _score
+from sklearn.metrics.scorer import check_scoring
+from sklearn.feature_selection.base import SelectorMixin
 
 
 class RFE(BaseEstimator, MetaEstimatorMixin, SelectorMixin):

### 2016-07-18 paper/paper.tex
added lasso to paper
changed names in paper

@@
 
-\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
-       \addr Department of Statistics\\
-       University of Washington\\
-       Seattle, WA 98195-4322, USA
+\author{\name Benjamin Rapier \u{a} \email benjamin.rabier@campus.tu-berlin.de \\
+       \addr Neural Information Processing Group\\
+       Technical University Berlin\\
+       10623 Berlin, Germany}
+
        \AND
-       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
-       \addr Division of Computer Science and Department of Statistics\\
-       University of California\\
-       Berkeley, CA 94720-1776, USA}
+       \name Alexander Goscinski \email a.goscinski@mail.tu-berlin.de \\
+       \addr Neural Information Processing Group\\
+       Technical University Berlin\\
+       10623 Berlin, Germany}
 
-\editor{Leslie Pack Kaelbling}
+\editor{No Editor}
 
@@
      \min_{w,b}  & \quad \frac12\|w\|^2 + C\sum_{i=1}^m \xi_i & & & \label{eq:svm_primal} \\ 
-   \text{s.\,t.} & \quad y^{(i)} (w^Tx^{i} + b) & \quad \geq & \quad 1 -\xi_i &&
+   \text{s.\,t.} & \quad y^{(i)} (w^Tx^{(i)} + b) & \quad \geq & \quad 1 -\xi_i &&
                    \quad \forall \, i = 1, \ldots, m \nonumber \\
@@
 of $1\%$ of all features was left.
+
+A form of Lasso
+
+\begin{equation}
+  \min_w \quad \frac1{2 \, \textrm{\#features}} \, \|y - Xw\|^2_2 + \alpha \, \|w\|_1
+\end{equation}
 
@@
 \appendix
-%\section*{Appendix A.}
-%\label{app:some appendix}
+\section*{Appendix A.}
+For the feature selection methods SU and RELIEF e used the scikit-feature library from \cite{Li-etal16}.
+\label{app:some appendix}
 

### 2016-07-23 experiments.py
Typos + .gitignore for LateX paper

@@ -200,7 +200,6 @@ class RawDataSetExperiment:
         write(2, [m.__name__ for m in self.benchmark.get_measures()])
 
 
-
 class EnsembleFMeasureExperiment(Experiment):
     def __init__(self, classifiers, data_set_feature_selectors, jaccard_percentage=0.01, beta=1):
         if not isinstance(data_set_feature_selectors, list):

### 2016-07-23 sklearn_rfe.py

@@ -141,8 +141,10 @@ class RFE(BaseEstimator, MetaEstimatorMixin, SelectorMixin):
             n_features_to_select = self.n_features_to_select
 
         if 0.0 < self.step < 1.0:
-            step = (int(max(1, self.step * n_features)) if not self.stepwise_selection
-                                                        else self.step)
+            if not self.stepwise_selection:
+                step = int(max(1, self.step * n_features))
+            else:
+                step = self.step    
         else:
             if self.stepwise_selection:
                 warnings.warn("The parameter 'stepwise_selection' is true but "

### 2016-07-23 data_sets.py
SVC_Grid & RFE in sklearn_utilities io_util.mkdir

@@ -1,9 +1,6 @@
-import matrix_io
-from sklearn import preprocessing
+import io_util
 import numpy as np
 import pandas as pd
-import os
-import errno
 import shutil
 
 
@@ -84,11 +81,7 @@ class DataSets:
 
         artificial_data_dir = DataSets.root_dir + "/ARTIFICIAL/ARTIFICIAL"
 
-        try:
-            os.makedirs(artificial_data_dir)
-        except OSError as exception:
-            if exception.errno != errno.EEXIST:
-                raise
+        io_util.mkdir(artificial_data_dir)
 
         data_file_name = artificial_data_dir + "/artificial.data"
         label_file_name = artificial_data_dir + "/artificial.labels"
@@ -114,7 +107,7 @@ class DataSets:
 
     @staticmethod
     def __load_data_set_file(info):
-        data = getattr(matrix_io, info.get('method', 'regular_matrix'))(
+        data = getattr(io_util, info.get('method', 'regular_matrix'))(
             DataSets.root_dir + info['path'],
             *info.get('args', []),
             **info.get('kwargs', {})

### 2016-07-23 experiments.py

@@ -4,9 +4,8 @@ from tabulate import tabulate
 import numpy as np
 import csv
 from data_sets import DataSets
-import os
 import sys
-import errno
+from io_util import mkdir
 
 
 class Experiment:
@@ -34,11 +33,7 @@ class Experiment:
     def save_results(self, file_name="output.csv", append=False):
         root_dir = DataSets.root_dir + "/results/" + type(self).__name__
 
-        try:
-            os.makedirs(root_dir)
-        except OSError as exception:
-            if exception.errno != errno.EEXIST:
-                raise
+        mkdir(root_dir)
 
         with open(root_dir + "/" + file_name, 'a' if append else 'w') as f:
             writer = csv.writer(f)
@@ -144,6 +139,8 @@ class DataSetExperiment(Experiment):
 
 
 class RawDataSetExperiment:
+    root_dir = DataSets.root_dir + "/results/RAW"
+
     def __init__(self, benchmark: Benchmark, data_set_feature_selectors):
         self.benchmark = benchmark
 
@@ -180,24 +177,18 @@ class RawDataSetExperiment:
         if filename is None:
             filename = type(self.benchmark).__name__
 
-        root_dir = DataSets.root_dir + "/results/RAW"
+        mkdir(self.root_dir)
 
-        try:
-            os.makedirs(root_dir)
-        except OSError as exception:
-            if exception.errno != errno.EEXIST:
-                raise
+        np.save("{}/{}.npy".format(self.root_dir, filename), self.results)
 
-        def write(dim, data):
-            with open("{}/{}_{}.txt".format(root_dir, filename, dim), "w") as f:
-                for d in data:
-                    f.write(d + "\n")
+        self.__write_dim_info(filename, 0, self.data_sets)
+        self.__write_dim_info(filename, 1, [f.__name__ for f in self.feature_selectors])
+        self.__write_dim_info(filename, 2, [m.__name__ for m in self.benchmark.get_measures()])
 
-        np.save("{}/{}.npy".format(root_dir, filename), self.results)
-
-        write(0, self.data_sets)
-        write(1, [f.__name__ for f in self.feature_selectors])
-        write(2, [m.__name__ for m in self.benchmark.get_measures()])
+    def __write_dim_info(self, filename, dim, data):
+        with open("{}/{}_{}.txt".format(self.root_dir, filename, dim), "w") as f:
+            for d in data:
+                f.write(d + "\n")
 
 
 class EnsembleFMeasureExperiment(Experiment):

### 2016-07-23 feature_selector.py

@@ -9,15 +9,12 @@ import skfeature.utility.mutual_information
 # Relief
 import skfeature.function.similarity_based.reliefF
 # SVM_RFE
-from sklearn.svm import SVC
-from sklearn.grid_search import GridSearchCV
-from sklearn_rfe import RFE
+from sklearn_utilities import RFE, SVC_Grid
 # Lasso
 from sklearn.linear_model import LassoCV
 from data_sets import DataSets, PreComputedData
 import multiprocessing
-import os
-import errno
+from io_util import mkdir
 
 
 class DataSetFeatureSelector(metaclass=ABCMeta):
@@ -128,11 +125,7 @@ class FeatureSelector(DataSetFeatureSelector, metaclass=ABCMeta):
             try:
                 cv_indices = PreComputedData.load_cv(data_set, cv)
             except FileNotFoundError:
-                try:
-                    os.makedirs(PreComputedData.cv_dir(data_set, cv))
-                except OSError as exception:
-                    if exception.errno != errno.EEXIST:
-                        raise
+                mkdir(PreComputedData.cv_dir(data_set, cv))
 
                 cv_indices = list(cv)
                 np.save(PreComputedData.cv_file_name(data_set, cv), cv_indices)
@@ -143,11 +136,7 @@ class FeatureSelector(DataSetFeatureSelector, metaclass=ABCMeta):
             return weights
 
     def __save(self, data_set, cv, method, feature_selection):
-        try:
-            os.makedirs(PreComputedData.dir_name(data_set, cv, method))
-        except OSError as exception:
-            if exception.errno != errno.EEXIST:
-                raise
+        mkdir(PreComputedData.dir_name(data_set, cv, method))
         np.save(PreComputedData.file_name(data_set, cv, method, self), feature_selection)
 
 
@@ -179,32 +168,15 @@ class Relief(FeatureSelector):
         return self.normalize(features_weight)
 
 
-class ClassifierFeatureSelector(FeatureSelector, metaclass=ABCMeta):
-    # TODO implement iterative grid search using scipy.stats.expon(scale=100) http://scikit-learn.org/stable/modules/grid_search.html
-    @staticmethod
-    def find_best_hyper_parameter(data, classes, classifier, parameter):
-        grid_search = GridSearchCV(
-            classifier,
-            {
-                parameter: [1, 10, 100, 1000]
-            },
-            cv=5,
-            scoring='precision'
[…]

### 2016-07-23 io_util.py

@@ -2,6 +2,8 @@ import numpy as np
 import csv
 from scipy.sparse import csr_matrix
 from scipy.io import loadmat
+import os
+import errno
 
 
 def matlab_matrix(path, **kwargs):
@@ -57,3 +59,11 @@ def sparse_binary_matrix(path, column_count, delimiter=' '):
                     indptr[-1] -= 1
 
     return csr_matrix((np.ones(len(indices)), indices, indptr), shape).T.toarray()
+
+
+def mkdir(path):
+    try:
+        os.makedirs(path)
+    except OSError as exception:
+        if exception.errno != errno.EEXIST:
+            raise

### 2016-07-23 sklearn_rfe.py

@@ -1,467 +1,0 @@
-# Authors: Alexandre Gramfort <alexandre.gramfort@inria.fr>
-#          Vincent Michel <vincent.michel@inria.fr>
-#          Gilles Louppe <g.louppe@gmail.com>
-#
-# License: BSD 3 clause
-
-"""Recursive feature elimination for feature ranking"""
-
-import warnings
-import numpy as np
-from sklearn.utils import check_X_y, safe_sqr
-from sklearn.utils.metaestimators import if_delegate_has_method
-from sklearn.base import BaseEstimator
-from sklearn.base import MetaEstimatorMixin
-from sklearn.base import clone
-from sklearn.base import is_classifier
-from sklearn.cross_validation import check_cv
-from sklearn.cross_validation import _safe_split, _score
-from sklearn.metrics.scorer import check_scoring
-from sklearn.feature_selection.base import SelectorMixin
-
-
-class RFE(BaseEstimator, MetaEstimatorMixin, SelectorMixin):
-    """Feature ranking with recursive feature elimination.
-
-    Given an external estimator that assigns weights to features (e.g., the
-    coefficients of a linear model), the goal of recursive feature elimination
-    (RFE) is to select features by recursively considering smaller and smaller
-    sets of features. First, the estimator is trained on the initial set of
-    features and weights are assigned to each one of them. Then, features whose
-    absolute weights are the smallest are pruned from the current set features.
-    That procedure is recursively repeated on the pruned set until the desired
-    number of features to select is eventually reached.
-
-    Read more in the :ref:`User Guide <rfe>`.
-
-    Parameters
-    ----------
-    estimator : object
-        A supervised learning estimator with a `fit` method that updates a
-        `coef_` attribute that holds the fitted parameters. Important features
-        must correspond to high absolute values in the `coef_` array.
-
-        For instance, this is the case for most supervised learning
-        algorithms such as Support Vector Classifiers and Generalized
-        Linear Models from the `svm` and `linear_model` modules.
-
-    n_features_to_select : int or None (default=None)
-        The number of features to select. If `None`, half of the features
-        are selected.
-
-    step : int or float, optional (default=1)
-        If greater than or equal to 1, then `step` corresponds to the (integer)
-        number of features to remove at each iteration.
-        If within (0.0, 1.0), then `step` corresponds to the percentage
-        (rounded down) of features to remove at each iteration.
-
-    estimator_params : dict
-        Parameters for the external estimator.
[…]

### 2016-07-23 sklearn_utilities.py

@@ -1,0 +1,153 @@
+import warnings
+import numpy as np
+from sklearn.utils import check_X_y, safe_sqr
+from sklearn.base import clone
+import sklearn.feature_selection
+from sklearn.grid_search import GridSearchCV
+from sklearn.svm import SVC
+
+
+class SVC_Grid:
+    """
+        SVC from scikit-learn with integrated Grid Search
+    """
+    def __init__(self, *args, **kwargs):
+        self.args = args
+        self.kwargs = kwargs
+        self.classifier = None
+
+    def fit(self, data, labels):
+        grid_search = GridSearchCV(
+            SVC(),
+            {
+                "C": [1, 10, 100, 1000]
+            },
+            cv=5,
+            scoring='precision'
+        )
+        grid_search.fit(data, labels)
+        self.kwargs["C"] = grid_search.best_params_["C"]
+
+        self.classifier = SVC(*self.args, **self.kwargs)
+
+        self.classifier.fit(data, labels)
+
+    def predict(self, data):
+        return self.classifier.predict(data)
+
+    def score(self, data, labels):
+        return self.classifier.score(data, labels)
+
+
+class RFE(sklearn.feature_selection.RFE):
+    """
+        RFE from scikit-learn with stepwise feature selection.
+
+        If enabled:
+        At each iteration (step * count of remaining features) are discarded
+        instead of (step * total count of features)
+    """
+    def __init__(self, *args, stepwise_selection=False, **kwargs):
+        super().__init__(*args, **kwargs)
+        self.stepwise_selection = stepwise_selection
+
+    def _fit(self, X, y, step_score=None):
+        X, y = check_X_y(X, y, "csc")
+        # Initialization
+        n_features = X.shape[1]
+        if self.n_features_to_select is None:
+            n_features_to_select = n_features // 2
+        else:
+            n_features_to_select = self.n_features_to_select
+
+        if 0.0 < self.step < 1.0:
+            if not self.stepwise_selection:
+                step = int(max(1, self.step * n_features))
+            else:
+                step = self.step    
+        else:
+            if self.stepwise_selection:
+                warnings.warn("The parameter 'stepwise_selection' is true but "
+                              "a fixed step size is given. Procedure will "
+                              " continue as if 'stepwise_selection' is false",
+                              RuntimeWarning)
+            step = int(self.step)
+        if step <= 0:
+            raise ValueError("Step must be >0")
+
+        if self.estimator_params is not None:
+            warnings.warn("The parameter 'estimator_params' is deprecated as "
[…]

### 2016-07-23 analysis.py
SVC_Grid extends SVC typical analysis functions in analysis.py mkdir in io_utils refactor static methods in artificial_data into simple methods without class

@@ -1,0 +1,121 @@
+from experiments import DataSetExperiment, RawDataSetExperiment
+from benchmarks import MeasureBenchmark, AccuracyBenchmark
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn_utilities import SVC_Grid
+from sklearn.ensemble import RandomForestClassifier
+import robustness_measure
+import goodness_measure
+import numpy as np
+from sklearn.cross_validation import KFold
+from sklearn.metrics import f1_score
+from data_sets import DataSets
+import sys
+
+default_classifiers = [
+    KNeighborsClassifier(3),
+    SVC_Grid(kernel="linear"),
+    RandomForestClassifier(max_depth=5, n_estimators=10, max_features=1)
+]
+
+
+def full(data_sets, feature_selectors, jaccard_percentage=0.01, classifiers=None, precision_measures=False):
+    if classifiers is None:
+        classifiers = default_classifiers
+
+    if isinstance(data_sets, str):
+        data_sets = [data_sets]
+
+    measures = [
+        robustness_measure.Spearman(),
+        robustness_measure.JaccardIndex(percentage=jaccard_percentage),
+    ]
+
+    accuracy_exp = DataSetExperiment(
+        AccuracyBenchmark(classifiers, percentage_of_features=jaccard_percentage),
+        feature_selectors
+    )
+
+    for data_set in data_sets:
+        print("Data Set: {}".format(data_set))
+
+        if precision_measures:
+            measures += [
+                goodness_measure.Precision(data_set),
+                goodness_measure.XPrecision(data_set)
+            ]
+
+        robustness_exp = DataSetExperiment(
+            MeasureBenchmark(measures),
+            feature_selectors
+        )
+
+        robustness_exp.run(data_set)
+        robustness_exp.print_results()
+        robustness_exp.save_results(data_set + "_rob.csv")
+
+        accuracy_exp.run(data_set)
+        accuracy_exp.print_results()
+        accuracy_exp.save_results(data_set + "_acc.csv")
+
+
+def raw(data_sets, feature_selectors, jaccard_percentage=0.01, classifiers=None):
+    if classifiers is None:
+        classifiers = default_classifiers
+
+    if isinstance(data_sets, str):
+        data_sets = [data_sets]
+
+    robustness_exp = RawDataSetExperiment(
+        MeasureBenchmark([
+            robustness_measure.JaccardIndex(percentage=jaccard_percentage),
+        ]),
[…]

### 2016-07-23 artificial_data.py

@@ -1,0 +1,93 @@
+import numpy as np
+
+
+def linear_labels(weights=None):
+    def labeling(samples, weights=weights):
+        if weights is None:
+            weights = np.random.uniform(-1, 1, samples.shape[0])
+        labels = weights.dot(samples)
+        return np.sign(labels - np.median(labels))
+
+    return labeling
+
+
+def linear_power_labels():
+    def labeling(samples):
+        powers = np.full(samples.shape[0], 2)
+        samples_power = np.power(samples.T, powers).T
+        return linear_labels()(samples_power)
+
+    return labeling
+
+
+def generate(n_samples, n_features, n_significant_features, feature_distribution,
+             noise_distribution=None,
+             insignificant_feature_distribution=None,
+             labeling=linear_labels()
+             ):
+    if n_significant_features <= 0 or n_significant_features > n_samples:
+        raise ValueError("significant needs to be positive and inferior to the number of samples")
+
+    if n_significant_features < 1:
+        n_significant_features = np.ceil(n_significant_features * n_features)
+
+    if insignificant_feature_distribution is None:
+        samples = feature_distribution((n_features, n_samples))
+    else:
+        samples = np.vstack((
+            feature_distribution((n_significant_features, n_samples)),
+            insignificant_feature_distribution((n_features - n_significant_features, n_samples))
+        ))
+
+    if noise_distribution:
+        samples += noise_distribution((n_features, n_samples))
+
+    labels = labeling(samples[:n_significant_features])
+
+    feature_labels = np.hstack((np.ones(n_significant_features),-np.ones(n_features-n_significant_features)))
+    return samples, labels, feature_labels
+
+
+def constant(c):
+    return lambda s: np.full(s, c)
+
+
+def uniform(a, b):
+    return lambda s: np.random.uniform(a, b, s)
+
+
+def laplace(mean, variance):
+    return lambda s: np.random.laplace(mean, variance, s)
+
+
+def normal(mean, variance):
+    return lambda s: np.random.normal(mean, variance, s)
+
+
+def multivariate_normal(mean, cov):
+    def distribution(s, mean=mean, cov=cov):
+        if callable(mean):
+            mean = mean(s[0])
+
+        if callable(cov):
+            cov = cov((s[0], s[0]))
+            # positive semi-definite matrix
+            cov = cov.T.dot(cov)
+
+        return np.random.multivariate_normal(mean, cov, s[1]).T
+
+    return distribution
+
+
[…]

### 2016-07-23 artificial_data_sets2.py

@@ -1,95 +1,0 @@
-import numpy as np
-
-
-class ArtificialLabels:
-    @staticmethod
-    def linear(weights=None):
-        def labeling(samples, weights=weights):
-            if weights is None:
-                weights = np.random.uniform(-1, 1, samples.shape[0])
-            labels = weights.dot(samples)
-            return np.sign(labels - np.median(labels))
-        return labeling
-
-    @staticmethod
-    def linear_power():
-        def labeling(samples):
-            powers = np.full(samples.shape[0], 2)
-            samples_power = np.power(samples.T, powers).T
-            return ArtificialLabels.linear()(samples_power)
-        return labeling
-
-
-class ArtificialData:
-    @staticmethod
-    def generate(n_samples, n_features, n_significant_features, feature_distribution,
-                 noise_distribution=None,
-                 insignificant_feature_distribution=None,
-                 labeling=ArtificialLabels.linear()
-                 ):
-        if n_significant_features <= 0 or n_significant_features > n_samples:
-            raise ValueError("significant needs to be positive and inferior to the number of samples")
-
-        if n_significant_features < 1:
-            n_significant_features = np.ceil(n_significant_features * n_features)
-
-        if insignificant_feature_distribution is None:
-            samples = feature_distribution((n_features, n_samples))
-        else:
-            samples = np.vstack((
-                feature_distribution((n_significant_features, n_samples)),
-                insignificant_feature_distribution((n_features - n_significant_features, n_samples))
-            ))
-
-        if noise_distribution:
-            samples += noise_distribution((n_features, n_samples))
-
-        labels = labeling(samples[:n_significant_features])
-
-        feature_labels = np.hstack((np.ones(n_significant_features),-np.ones(n_features-n_significant_features)))
-        return samples, labels, feature_labels
-
-    @staticmethod
-    def constant(c):
-        return lambda s: np.full(s, c)
-
-    @staticmethod
-    def uniform(a, b):
-        return lambda s: np.random.uniform(a, b, s)
-
-    @staticmethod
-    def laplace(mean, variance):
-        return lambda s: np.random.laplace(mean, variance, s)
-
-    @staticmethod
-    def normal(mean, variance):
-        return lambda s: np.random.normal(mean, variance, s)
-
-    @staticmethod
-    def multivariate_normal(mean, cov):
-        def distribution(s, mean=mean, cov=cov):
-            if callable(mean):
-                mean = mean(s[0])
-
-            if callable(cov):
[…]

### 2016-07-23 data_sets.py

@@ -1,4 +1,4 @@
-import io_util
+import io_utils
 import numpy as np
 import pandas as pd
 import shutil
@@ -81,7 +81,7 @@ class DataSets:
 
         artificial_data_dir = DataSets.root_dir + "/ARTIFICIAL/ARTIFICIAL"
 
-        io_util.mkdir(artificial_data_dir)
+        io_utils.mkdir(artificial_data_dir)
 
         data_file_name = artificial_data_dir + "/artificial.data"
         label_file_name = artificial_data_dir + "/artificial.labels"
@@ -107,7 +107,7 @@ class DataSets:
 
     @staticmethod
     def __load_data_set_file(info):
-        data = getattr(io_util, info.get('method', 'regular_matrix'))(
+        data = getattr(io_utils, info.get('method', 'regular_matrix'))(
             DataSets.root_dir + info['path'],
             *info.get('args', []),
             **info.get('kwargs', {})

### 2016-07-23 experiments.py

@@ -5,7 +5,7 @@ import numpy as np
 import csv
 from data_sets import DataSets
 import sys
-from io_util import mkdir
+from io_utils import mkdir
 
 
 class Experiment:
@@ -162,14 +162,18 @@ class RawDataSetExperiment:
         for i, data_set in enumerate(data_sets):
             print(data_set)
             data, labels = DataSets.load(data_set)
-            self.results.append([])
+            result = []
+
             for feature_selector in self.feature_selectors:
                 print(feature_selector.__name__)
-                self.results[i].append(self.benchmark.run_raw_result(
+                result.append(self.benchmark.run_raw_result(
                     data,
                     labels,
                     feature_selector.rank_data_set(data_set, self.benchmark.cv)
                 ))
+
+            self.results.append(result)
+
         self.results = np.array(self.results)
         return self.results
 

### 2016-07-23 feature_selector.py

@@ -10,11 +10,12 @@ import skfeature.utility.mutual_information
 import skfeature.function.similarity_based.reliefF
 # SVM_RFE
 from sklearn_utilities import RFE, SVC_Grid
+import sklearn.feature_selection
 # Lasso
 from sklearn.linear_model import LassoCV
 from data_sets import DataSets, PreComputedData
 import multiprocessing
-from io_util import mkdir
+from io_utils import mkdir
 
 
 class DataSetFeatureSelector(metaclass=ABCMeta):
@@ -174,23 +175,22 @@ class SVM_RFE(FeatureSelector):
         self.step = step
 
     def weight(self, data, labels):
-        rfe = RFE(
+        rfe = sklearn.feature_selection.RFE(
             estimator=SVC_Grid(
                 kernel='linear',
             ),
             n_features_to_select=round(len(data) * 0.01),
-            step=self.step,
-            stepwise_selection=True
+            step=self.step
         )
         rfe.fit(data.T, labels)
+
         ordered_ranks = self.reverse_order(rfe.ranking_)
 
         return self.normalize(ordered_ranks)
 
     @staticmethod
     def reverse_order(ranks):
-        ordered_ranks = -ranks + np.max(ranks) + 1
-        return ordered_ranks
+        return -ranks + np.max(ranks) + 1
 
 
 class LassoFeatureSelector(FeatureSelector):

### 2016-07-23 sklearn_utilities.py

@@ -7,16 +7,11 @@ from sklearn.grid_search import GridSearchCV
 from sklearn.svm import SVC
 
 
-class SVC_Grid:
+class SVC_Grid(SVC):
     """
         SVC from scikit-learn with integrated Grid Search
     """
-    def __init__(self, *args, **kwargs):
-        self.args = args
-        self.kwargs = kwargs
-        self.classifier = None
-
-    def fit(self, data, labels):
+    def fit(self, data, labels, sample_weight=None):
         grid_search = GridSearchCV(
             SVC(),
             {
@@ -26,17 +21,9 @@ class SVC_Grid:
             scoring='precision'
         )
         grid_search.fit(data, labels)
-        self.kwargs["C"] = grid_search.best_params_["C"]
+        self.C = grid_search.best_params_["C"]
 
-        self.classifier = SVC(*self.args, **self.kwargs)
-
-        self.classifier.fit(data, labels)
-
-    def predict(self, data):
-        return self.classifier.predict(data)
-
-    def score(self, data, labels):
-        return self.classifier.score(data, labels)
+        super(SVC, self).fit(data, labels, sample_weight)
 
 
 class RFE(sklearn.feature_selection.RFE):

### 2016-07-23 test.py

@@ -1,57 +1,9 @@
-from experiments import *
 from feature_selector import SymmetricalUncertainty, Relief, SVM_RFE, LassoFeatureSelector, Random, FeatureSelector
-import robustness_measure
-import goodness_measure
 import ensemble_methods
-# classifiers
-from sklearn.neighbors import KNeighborsClassifier
-from sklearn.svm import SVC
-from sklearn.ensemble import RandomForestClassifier
-from artificial_data_sets2 import ArtificialData, ArtificialLabels
-from sklearn.grid_search import GridSearchCV
-
-feature_selectors = [
-    SymmetricalUncertainty(),
-    Relief(),
-    SVM_RFE(),
-    LassoFeatureSelector(),
-]
-
-
-class SVC_Grid:
-    def __init__(self, *args, **kwargs):
-        self.args = args
-        self.kwargs = kwargs
-        self.classifier = None
-
-    def fit(self, data, labels):
-        grid_search = GridSearchCV(
-            SVC(),
-            {
-                "C": [1, 10, 100, 1000]
-            },
-            cv=5,
-            scoring='precision'
-        )
-        grid_search.fit(data, labels)
-        self.kwargs["C"] = grid_search.best_params_["C"]
-
-        self.classifier = SVC(*self.args, **self.kwargs)
-
-        self.classifier.fit(data, labels)
-
-    def predict(self, data):
-        return self.classifier.predict(data)
-
-    def score(self, data, labels):
-        return self.classifier.score(data, labels)
-
-
-classifiers = [
-    KNeighborsClassifier(3),
-    SVC_Grid(kernel="linear"),
-    RandomForestClassifier(max_depth=5, n_estimators=10, max_features=1)
-]
+import analysis
+import artificial_data
+import numpy as np
+from data_sets import DataSets
 
 import warnings
 
@@ -60,128 +12,45 @@ warnings.filterwarnings('ignore')
 # total_features = 1e4
 # n_significant_features = int(total_features*0.01)
 # DataSets.save_artificial(
-#     *ArtificialData.generate(
+#     *artificial_data.generate(
 #         n_samples=300,
 #         n_features=total_features,
 #         n_significant_features=n_significant_features,
-#         feature_distribution=ArtificialData.multivariate_normal(
[…]

### 2016-07-23 feature_selector.py
use RFE with setpwise selection

@@ -10,7 +10,6 @@ import skfeature.utility.mutual_information
 import skfeature.function.similarity_based.reliefF
 # SVM_RFE
 from sklearn_utilities import RFE, SVC_Grid
-import sklearn.feature_selection
 # Lasso
 from sklearn.linear_model import LassoCV
 from data_sets import DataSets, PreComputedData
@@ -142,8 +141,6 @@ class FeatureSelector(DataSetFeatureSelector, metaclass=ABCMeta):
 
 
 class Dummy(FeatureSelector):
-    __name__ = "Dummy"
-
     def rank(self, data, labels):
         return np.arange(data.shape[0])
 
@@ -175,7 +172,7 @@ class SVM_RFE(FeatureSelector):
         self.step = step
 
     def weight(self, data, labels):
-        rfe = sklearn.feature_selection.RFE(
+        rfe = RFE(
             estimator=SVC_Grid(
                 kernel='linear',
             ),
@@ -208,11 +205,6 @@ class LassoFeatureSelector(FeatureSelector):
 
 
 class Random(FeatureSelector):
-    # def rank(self, data, labels):
-    #     features_rank = np.arange(1, len(data) + 1)
-    #     np.random.shuffle(features_rank)
-    #     return features_rank
-
     def weight(self, data, labels):
         weights = np.random.uniform(0, 1, len(data))
         return weights

### 2016-07-23 artificial_data.py
typo

@@ -1,7 +1,7 @@
 import numpy as np
 
 
-def linear_labels(weights=None):
+def linear_labeling(weights=None):
     def labeling(samples, weights=weights):
         if weights is None:
             weights = np.random.uniform(-1, 1, samples.shape[0])
@@ -11,11 +11,11 @@ def linear_labels(weights=None):
     return labeling
 
 
-def linear_power_labels():
+def linear_power_labeling():
     def labeling(samples):
         powers = np.full(samples.shape[0], 2)
         samples_power = np.power(samples.T, powers).T
-        return linear_labels()(samples_power)
+        return linear_labeling()(samples_power)
 
     return labeling
 
@@ -23,7 +23,7 @@ def linear_power_labels():
 def generate(n_samples, n_features, n_significant_features, feature_distribution,
              noise_distribution=None,
              insignificant_feature_distribution=None,
-             labeling=linear_labels()
+             labeling=linear_labeling()
              ):
     if n_significant_features <= 0 or n_significant_features > n_samples:
         raise ValueError("significant needs to be positive and inferior to the number of samples")

### 2016-07-23 test.py

@@ -25,7 +25,7 @@ warnings.filterwarnings('ignore')
 #             shares=[0.5, 0.5]
 #         ),
 #         noise_distribution=artificial_data.normal(0, 0.05),
-#         labeling=artificial_data.linear_labels(weights=np.ones(n_significant_features))
+#         labeling=artificial_data.linear_labeling(weights=np.ones(n_significant_features))
 #     )
 # )
 

### 2016-07-23 feature_selector.py
SVM_RFE: percentage of features to select parameter

@@ -167,16 +167,17 @@ class Relief(FeatureSelector):
 
 
 class SVM_RFE(FeatureSelector):
-    def __init__(self, step=0.1):
+    def __init__(self, step=0.1, percentage_features_to_select=0.01):
         super().__init__()
         self.step = step
+        self.percentage_features_to_select = percentage_features_to_select
 
     def weight(self, data, labels):
         rfe = RFE(
             estimator=SVC_Grid(
                 kernel='linear',
             ),
-            n_features_to_select=round(len(data) * 0.01),
+            n_features_to_select=round(data.shape[0] * self.percentage_features_to_select),
             step=self.step
         )
         rfe.fit(data.T, labels)

### 2016-07-23 analysis.py
Balanced Error Rate in accuracy_measure Possibility to specify an accuracy measure in AccuracyBenchmark LogisticRegressionCV used as classifier and feature selectors RawDataSetExperiment print mean results during computation

@@ -3,6 +3,7 @@ from benchmarks import MeasureBenchmark, AccuracyBenchmark
 from sklearn.neighbors import KNeighborsClassifier
 from sklearn_utilities import SVC_Grid
 from sklearn.ensemble import RandomForestClassifier
+from sklearn.linear_model import LogisticRegressionCV
 import robustness_measure
 import goodness_measure
 import numpy as np
@@ -14,7 +15,8 @@ import sys
 default_classifiers = [
     KNeighborsClassifier(3),
     SVC_Grid(kernel="linear"),
-    RandomForestClassifier(max_depth=5, n_estimators=10, max_features=1)
+    RandomForestClassifier(max_depth=5, n_estimators=10, max_features=1),
+    LogisticRegressionCV(penalty='l1', solver='liblinear')
 ]
 
 
@@ -77,11 +79,12 @@ def raw(data_sets, feature_selectors, jaccard_percentage=0.01, classifiers=None)
         feature_selectors
     )
 
+    jcp = int(jaccard_percentage * 1e3)
     robustness_exp.run(data_sets)
-    robustness_exp.save_results("jc{}_robustness".format(jaccard_percentage * 1e3))
+    robustness_exp.save_results("jc{}_robustness".format(jcp))
 
     accuracy_exp.run(data_sets)
-    accuracy_exp.save_results("jc{}_accuracy".format(jaccard_percentage * 1e3))
+    accuracy_exp.save_results("jc{}_accuracy".format(jcp))
 
 
 def without_feature_selectors(data_sets, classifiers):

### 2016-07-23 benchmarks.py

@@ -5,8 +5,9 @@ import multiprocessing
 import ctypes
 from feature_selector import FeatureSelector
 from robustness_measure import Measure, JaccardIndex
-from sklearn.metrics import f1_score
+from sklearn.base import clone as clone_classifier
 from collections import Iterable
+from accuracy_measure import ber
 
 
 class Benchmark(metaclass=ABCMeta):
@@ -88,19 +89,23 @@ class MeasureBenchmark(Benchmark):
 
 
 class ClassifierWrapper:
-    def __init__(self, classifier):
+    def __init__(self, classifier, accuracy_measure):
         self.classifier = classifier
         self.__name__ = type(classifier).__name__
+        self.accuracy_measure = accuracy_measure
 
     def run_and_set_in_results(self, data, labels, train_index, test_index, results, result_index):
         np.random.seed()
-        self.classifier.fit(
+        classifier = clone_classifier(self.classifier)
+
+        classifier.fit(
             data[:, train_index].T,
             labels[train_index]
         )
-        results[result_index] = f1_score(
+
+        results[result_index] = self.accuracy_measure(
             labels[test_index],
-            self.classifier.predict(data[:, test_index].T)
+            classifier.predict(data[:, test_index].T)
         )
 
 
@@ -108,7 +113,9 @@ class AccuracyBenchmark(Benchmark):
     percentage_of_features = 0.01
     n_fold = 10
 
-    def __init__(self, classifiers, feature_selector: FeatureSelector = None, percentage_of_features=None):
+    def __init__(self, classifiers, feature_selector: FeatureSelector = None, percentage_of_features=None,
+                 accuracy_measure=ber
+                 ):
         self.feature_selector = feature_selector
 
         if percentage_of_features is not None:
@@ -117,7 +124,7 @@ class AccuracyBenchmark(Benchmark):
         if not isinstance(classifiers, list):
             classifiers = [classifiers]
 
-        self.classifiers = [ClassifierWrapper(c) for c in classifiers]
+        self.classifiers = [ClassifierWrapper(c, accuracy_measure) for c in classifiers]
 
     def run_raw_result(self, data, labels, features_selection=None):
         if features_selection is None:

### 2016-07-23 experiments.py

@@ -13,31 +13,32 @@ class Experiment:
     row_labels = []
     col_labels = []
 
-    @property
-    def results_table(self):
+    @staticmethod
+    def results_table(rows_label, cols_label, results):
         rows = [
-            ["Measure"] + self.col_labels
+            ["Measure"] + cols_label
         ]
-        for i in range(self.results.shape[0]):
-            row = [self.row_labels[i]]
-            row += map(lambda i: "{:.2%}".format(i), self.results[i, :].tolist())
+        for i in range(results.shape[0]):
+            row = [rows_label[i]]
+            row += map(lambda i: "{:.2%}".format(i), results[i, :].tolist())
             rows.append(row)
 
         return rows
 
     def print_results(self):
-        rows = self.results_table
-        print(tabulate(rows[1:len(rows)], rows[0], tablefmt='pipe'))
+        table = self.results_table(self.row_labels, self.col_labels, self.results)
+        print(tabulate(table[1:len(table)], table[0], tablefmt='pipe'))
         print()
 
     def save_results(self, file_name="output.csv", append=False):
         root_dir = DataSets.root_dir + "/results/" + type(self).__name__
+        table = self.results_table(self.row_labels, self.col_labels, self.results)
 
         mkdir(root_dir)
 
         with open(root_dir + "/" + file_name, 'a' if append else 'w') as f:
             writer = csv.writer(f)
-            writer.writerows(self.results_table)
+            writer.writerows(table)
 
 
 class MeasureExperiment(Experiment):
@@ -155,26 +156,43 @@ class RawDataSetExperiment:
         self.results = None
         self.data_sets = None
 
+        self.row_labels = [m.__name__ for m in self.benchmark.get_measures()]
+        self.col_labels = [f.__name__ for f in self.feature_selectors]
+
     def run(self, data_sets):
         self.results = []
         self.data_sets = data_sets
+        bc_name = type(self.benchmark).__name__
 
         for i, data_set in enumerate(data_sets):
-            print(data_set)
             data, labels = DataSets.load(data_set)
             result = []
 
             for feature_selector in self.feature_selectors:
-                print(feature_selector.__name__)
+                sys.stdout.write("\rRAW {} progress: {} [{}]".format(
+                    bc_name,
+                    data_set,
+                    feature_selector.__name__
+                ))
+
                 result.append(self.benchmark.run_raw_result(
                     data,
                     labels,
[…]

### 2016-07-23 feature_selector.py

@@ -11,7 +11,7 @@ import skfeature.function.similarity_based.reliefF
 # SVM_RFE
 from sklearn_utilities import RFE, SVC_Grid
 # Lasso
-from sklearn.linear_model import LassoCV
+from sklearn.linear_model import LogisticRegressionCV
 from data_sets import DataSets, PreComputedData
 import multiprocessing
 from io_utils import mkdir
@@ -192,17 +192,10 @@ class SVM_RFE(FeatureSelector):
 
 
 class LassoFeatureSelector(FeatureSelector):
-    def rank(self, data, labels):
-        lasso = LassoCV(cv=2, normalize=True)
-        lasso.fit(data.T, labels)
-        features_rank = self.rank_weights(np.abs(lasso.coef_))
-        return features_rank
-
     def weight(self, data, labels):
-        lasso = LassoCV(cv=2, normalize=True)
+        lasso = LogisticRegressionCV(penalty='l1', solver='liblinear')
         lasso.fit(data.T, labels)
-        normalized = self.normalize(np.abs(lasso.coef_))
-        return normalized
+        return self.normalize(np.abs(lasso.coef_[0]))
 
 
 class Random(FeatureSelector):

### 2016-07-23 experiments.py
Replace sys.stdout.write by print

@@ -4,7 +4,6 @@ from tabulate import tabulate
 import numpy as np
 import csv
 from data_sets import DataSets
-import sys
 from io_utils import mkdir
 
 
@@ -169,7 +168,7 @@ class RawDataSetExperiment:
             result = []
 
             for feature_selector in self.feature_selectors:
-                sys.stdout.write("\rRAW {} progress: {} [{}]".format(
+                print("RAW {} progress: {} [{}]".format(
                     bc_name,
                     data_set,
                     feature_selector.__name__
@@ -185,11 +184,11 @@ class RawDataSetExperiment:
             self.results.append(result)
             table = Experiment.results_table(self.row_labels, self.col_labels, result.mean(axis=-1).T)
 
-            sys.stdout.write("\rRAW {} : {}\n".format(bc_name, data_set))
+            print("RAW {} : {}".format(bc_name, data_set))
             print(tabulate(table[1:len(table)], table[0], tablefmt='pipe'))
             print()
 
-        sys.stdout.write("\rRAW {} done\n".format(bc_name))
+        print("RAW {} done".format(bc_name))
 
         self.results = np.array(self.results)
 
@@ -244,7 +243,7 @@ class EnsembleFMeasureExperiment(Experiment):
             data, labels = DataSets.load(data_set)
 
             for j, feature_selector in enumerate(self.feature_selectors):
-                sys.stdout.write("\rProgress: {:.2%}".format((i * len_fs + j)/size))
+                print("Progress: {:.2%}".format((i * len_fs + j)/size))
                 self.results[i, j] = benchmark.run(
                     data,
                     labels,

### 2016-07-23 analysis.py
Use ber instead of f1_score for accuracy with all features

@@ -11,6 +11,7 @@ from sklearn.cross_validation import KFold
 from sklearn.metrics import f1_score
 from data_sets import DataSets
 import sys
+from accuracy_measure import ber
 
 default_classifiers = [
     KNeighborsClassifier(3),
@@ -108,7 +109,7 @@ def without_feature_selectors(data_sets, classifiers):
                     data[:, train_index].T,
                     labels[train_index]
                 )
-                results[i, j, k] = f1_score(
+                results[i, j, k] = ber(
                     labels[test_index],
                     classifier.predict(data[:, test_index].T)
                 )

### 2016-07-24 analysis.py
SU gives normalized weights rankings are not saved anymore

@@ -8,7 +8,6 @@ import robustness_measure
 import goodness_measure
 import numpy as np
 from sklearn.cross_validation import KFold
-from sklearn.metrics import f1_score
 from data_sets import DataSets
 import sys
 from accuracy_measure import ber

### 2016-07-24 experiments.py

@@ -168,7 +168,7 @@ class RawDataSetExperiment:
             result = []
 
             for feature_selector in self.feature_selectors:
-                print("RAW {} progress: {} [{}]".format(
+                print("RAW {}: {} [{}]".format(
                     bc_name,
                     data_set,
                     feature_selector.__name__
@@ -184,7 +184,7 @@ class RawDataSetExperiment:
             self.results.append(result)
             table = Experiment.results_table(self.row_labels, self.col_labels, result.mean(axis=-1).T)
 
-            print("RAW {} : {}".format(bc_name, data_set))
+            print("\n{}".format(data_set.upper()))
             print(tabulate(table[1:len(table)], table[0], tablefmt='pipe'))
             print()
 

### 2016-07-24 feature_selector.py

@@ -37,7 +37,7 @@ class DataSetFeatureSelector(metaclass=ABCMeta):
         self.check_data_set_and_cv(data_set, cv_generator)
 
     @staticmethod
-    def normalize(vector):
+    def normalize(vector: np.ndarray):
         return preprocessing.MinMaxScaler().fit_transform(vector)
 
     @staticmethod
@@ -92,18 +92,9 @@ class FeatureSelector(DataSetFeatureSelector, metaclass=ABCMeta):
     def rank_data_set(self, data_set, cv_generator):
         super().rank_data_set(data_set, cv_generator)
 
-        data, labels = DataSets.load(data_set)
-        cv = cv_generator(labels.shape[0])
+        weights = self.weight_data_set(data_set, cv_generator)
 
-        try:
-            return PreComputedData.load(data_set, cv, "rank", self)
-        except FileNotFoundError:
-            weights = self.weight_data_set(data_set, cv_generator)
-
-            ranks = np.array([self.rank_weights(w) for w in weights])
-            self.__save(data_set, cv, "rank", ranks)
-
-            return ranks
+        return np.array([self.rank_weights(w) for w in weights])
 
     def weight_data_set(self, data_set, cv_generator):
         super().weight_data_set(data_set, cv_generator)
@@ -156,7 +147,7 @@ class SymmetricalUncertainty(FeatureSelector):
             features_weight.append(
                 skfeature.utility.mutual_information.su_calculation(data[i], labels)
             )
-        return np.array(features_weight)
+        return self.normalize(np.array(features_weight))
 
 
 class Relief(FeatureSelector):

### 2016-07-24 paper/paper.tex
Zeilenabstand fixed
Evaluation section

@@
 \usepackage{amsmath}
+\usepackage{enumitem}
 
@@
 
-\author{\name Benjamin Rapier \u{a} \email benjamin.rabier@campus.tu-berlin.de \\
+\author{\name Benjamin Rapier \email benjamin.rabier@campus.tu-berlin.de \\
        \addr Neural Information Processing Group\\
        Technical University Berlin\\
-       10623 Berlin, Germany}
-
+       10623 Berlin, Germany
        \AND
@@
 
-Feature selection is a preprocessing step used in machine learning application to find
-a small subset of features in order to build a more accurate, simpler and faster model.
-Moreover it allows domain experts to gain a better understanding of the data, by focusing
-on the selected subset.However in domains such as biomedical applications, 
-where subsequent analysis are costly, not only the model performance but also the robustness
-of the feature selection method is important. Domain experts would prefer a more stable
-algorithm to have more confidence in the selected features. One approach for more robust
-results are ensemble methods.
+Feature selection is a preprocessing step used in machine learning application to find a small subset of features in order to build a more accurate, simpler and faster model.
+Moreover it allows domain experts to gain a better understanding of the data, by focusing on the selected subset.
+However, in domains such as biomedical applications subsequent analysis are costly.
+Therefore not only the model performance but also the robustness of the feature selection method is important.
+Domain experts would prefer a more stable algorithm to have more confidence in the selected features.
+One approach for more robust results are ensemble methods.
 
-In ensemble learning multiple algorithms are combined to obtain better performance or stability.
-We build on the work of \cite{saeys2008} who applied ensemble learning by using
-the same feature selector on different subsets. In this work we investigate the effect of ensemble methods
-further by using multiple feature selection methods. 
-In order to find a good trade-off between robustness and model performance, multiple feature selection methods were
-combined in multiple ways.
+Used in Machine Learning and Statistics, ensemble methods combine multiple algorithms in order to obtain better performance.
+We build on the work of \cite{saeys2008} who applied ensemble learning by using the same feature selector on different subsets.
+In this work we investigate the effect of ensemble methods further by combining different feature selection methods.
 
@@
 \section{Ensemble methods}
-%Weighting
-We first calculate the weights if avaible by the features selector otherwise the ranks.
-For feature selector, which do not omit normalized weights between a0 and 1, we normalize
-the weights to the range $[0,1]$. We also normalize the ranks of the features selectors returning
-ranks to the range $[0,1]$. Now that we combine the weights after one of the following rules: \ldots
 
-Ensemble method: The weights of different feature selection methods are first computed and then linearly aggregated to obtain the new weights. Three methods were used:
-The mean is used as the new weight.
-The minimum, maximum and the mean are linearly aggregated.
-The accuracy is estimated for each of the feature selector for multiple classifiers.
-Then the different feature weights are accordingly weighted to favor the feature selector with the best performance and the previous method is applied.
+Different feature selection methods are combined by aggregating the weight they give for each feature regarding importance.
+Since different methods do not always have the same weight range, they are normalized to the range $[0,1]$.
+Moreover for the methods which can only rank data, such as methods based on RFE, their ranking are considered as weights, and so subsequently normalized the same way.
 
-\section{Results}
+Those normalized weights are combined using different techniques. The methods used in this paper can be grouped in three distinct categories:
+
+\begin{description}[align=left]
+\item [Linear aggregation :] The average of the weights was taken as the new weight.
+\item [Non-linear aggregation :] Two methods were used, first averaging powers of the weights and secondly aggregating linearly the minimum, maximum and the average of the weights.
+\item [Performance related aggregation :] For each feature selector the best 1\% of the features were selected and used to measure the classification performance for multiple classifiers.
+The feature selection methods result were weighted accordingly to their accuracy.
+\end{description}
+
+\section{Evaluation}
+
+While the purpose of this paper is to find a robust feature selection method, it is also necessary to evaluate the classification performance as domain export have no interest in badly performing model.
+Hence those two aspects are always considered in combination
+
+\subsection{Data Sets}
+Datasets are taken from the NIPS 2003 challenge \cite{NIPS}.
+However, due to computation power constraints not the whole dataset is always used.
+Additionally the colon data set \cite{alon1999broad} is used.
+Finally artificial data is also generated, since it is possible to control which features are meaningful.
+
+\begin{center}
+    \begin{tabular}{| r | c | c | c | c | c |}
+    \hline
+    Name & \# Samples & \# Features & \# Class 1 & \# Class 2 & Ref\\ \hline
+    Arcene & 200 & 10 000 & 112 & 88 & \cite{NIPS} \\
+    Dexter & 600 & 20 000 & 300 & 300 & \cite{NIPS} \\
+    Gisette & 200 & 5000 & 92 & 108 & \cite{NIPS} \\
+    Colon & 62 & 2000 & 40 & 22 &  \cite{alon1999broad} \\
+    Artificial & 300 & 10 000 & 150 & 150 & \\
+    \hline
+    \end{tabular}
+\end{center}
+
+The features of the artificial dataset are generated with two distributions, depending on whether they are used in the labeling process or not.
+
+\begin{align}
+\text{significant} \quad & f \sim N(0, \Sigma) \quad \text{with} \quad \Sigma_{ij} \sim U(-1,1) \\
+\text{unsignificant} \quad & f \sim 0.5 * \left[ N(0, 1) + U(-1,1) \right]
+\end{align}
+
+To generate balanced binary labels, the significant features are first summed, then the median of the sums is subtracted, finally the sign is taken.
+
+\subsection{Experiments}
+
+The robustness is evaluated with a ShuffleSplit of 10 folds with 90\% of the data, as the number of samples is already limited.
+After weighting the features the best ones are taken (from 0.1\% to 1\%) and those subsets are compared with the Jaccard Index.
+For two subsets of features $F_i$ and $F_j$ it is defined as:
+
+\begin{equation}
+J(F_i, F_j) = \frac{| F_i \cap F_j |}{| F_i \cup F_j |}
+\end{equation}
+
+The classification performance is estimated with a cross validation of 10 folds with multiple classifiers, trained and tested on the subset of features.
+4 different classifiers are used: Lasso, linear SVM, k-nearest neighbor, Random Forest.
+
+\subsection{Results}
 - Do SVM\_RFE with exponential rising

### 2016-07-24 experiments.py
RAW results table (with std)

@@ -24,6 +24,19 @@ class Experiment:
 
         return rows
 
+    @staticmethod
+    def raw_results_table(rows_label, cols_label, mean, std):
+        rows = [
+            ["Measure"] + cols_label
+        ]
+        std /= 2
+        for i in range(mean.shape[0]):
+            row = [rows_label[i]]
+            row += map(lambda m, s: "{:.2%} ± {:.2%}".format(m, s), mean[i, :].tolist(), std[i, :].tolist())
+            rows.append(row)
+
+        return rows
+
     def print_results(self):
         table = self.results_table(self.row_labels, self.col_labels, self.results)
         print(tabulate(table[1:len(table)], table[0], tablefmt='pipe'))
@@ -182,7 +195,12 @@ class RawDataSetExperiment:
 
             result = np.array(result)
             self.results.append(result)
-            table = Experiment.results_table(self.row_labels, self.col_labels, result.mean(axis=-1).T)
+            table = Experiment.raw_results_table(
+                self.row_labels,
+                self.col_labels,
+                result.mean(axis=-1).T,
+                result.std(axis=-1).T
+            )
 
             print("\n{}".format(data_set.upper()))
             print(tabulate(table[1:len(table)], table[0], tablefmt='pipe'))

### 2016-07-24 feature_selector.py
SVM_RFE name include step & percentage of feature to select

@@ -162,6 +162,7 @@ class SVM_RFE(FeatureSelector):
         super().__init__()
         self.step = step
         self.percentage_features_to_select = percentage_features_to_select
+        self.__name__ = "SVM_RFE_by_{:.1}_until_{:.1}".format(step, percentage_features_to_select)
 
     def weight(self, data, labels):
         rfe = RFE(

### 2016-07-28 analysis.py
RawDataSetExperiment becomes DataSetExperiment analysis: function for artificial data_set analysis: full and raw becomes run

@@ -1,4 +1,4 @@
-from experiments import DataSetExperiment, RawDataSetExperiment
+from experiments import DataSetExperiment
 from benchmarks import MeasureBenchmark, AccuracyBenchmark
 from sklearn.neighbors import KNeighborsClassifier
 from sklearn_utilities import SVC_Grid
@@ -16,81 +16,88 @@ default_classifiers = [
 ]
 
 
-def full(data_sets, feature_selectors, jaccard_percentage=0.01, classifiers=None, precision_measures=False):
-    if classifiers is None:
-        classifiers = default_classifiers
-
+def run(data_sets, feature_selectors, jaccard_percentage=0.01, classifiers=None,
+        measures=None, save=True, prefix=""):
     if isinstance(data_sets, str):
         data_sets = [data_sets]
 
-    measures = [
-        robustness_measure.Spearman(),
-        robustness_measure.JaccardIndex(percentage=jaccard_percentage),
-    ]
+    if classifiers is None:
+        classifiers = default_classifiers
+
+    if measures is None:
+        measures = [
+            robustness_measure.JaccardIndex(percentage=jaccard_percentage)
+        ]
+
+    if len(prefix) > 0:
+        prefix += "_"
+
+    robustness_exp = DataSetExperiment(
+        MeasureBenchmark(measures),
+        feature_selectors
+    )
 
     accuracy_exp = DataSetExperiment(
         AccuracyBenchmark(classifiers, percentage_of_features=jaccard_percentage),
         feature_selectors
     )
 
-    for data_set in data_sets:
-        print("Data Set: {}".format(data_set))
+    jcp = int(jaccard_percentage * 1e3)
+    robustness_exp.run(data_sets)
+    if save:
+        robustness_exp.save_results(prefix + "jc{}_robustness".format(jcp))
 
-        if precision_measures:
-            measures += [
-                goodness_measure.Precision(data_set),
-                goodness_measure.XPrecision(data_set)
-            ]
-
-        robustness_exp = DataSetExperiment(
-            MeasureBenchmark(measures),
-            feature_selectors
-        )
-
-        robustness_exp.run(data_set)
-        robustness_exp.print_results()
-        robustness_exp.save_results(data_set + "_rob.csv")
-
-        accuracy_exp.run(data_set)
-        accuracy_exp.print_results()
-        accuracy_exp.save_results(data_set + "_acc.csv")
[…]

### 2016-07-28 experiments.py

@@ -116,42 +116,7 @@ class AccuracyExperiment(Experiment):
         super().print_results()
 
 
-class DataSetExperiment(Experiment):
-    def __init__(self, benchmark: Benchmark, data_set_feature_selectors):
-        self.benchmark = benchmark
-
-        if not isinstance(data_set_feature_selectors, list):
-            data_set_feature_selectors = [data_set_feature_selectors]
-
-        for data_set_feature_selector in data_set_feature_selectors:
-            if not isinstance(data_set_feature_selector, DataSetFeatureSelector):
-                raise ValueError("Only DataSetFeatureSelector can be used")
-
-        self.feature_selectors = data_set_feature_selectors
-
-        self.results = np.zeros((len(benchmark.get_measures()), len(self.feature_selectors)))
-
-        self.row_labels = [m.__name__ for m in self.benchmark.get_measures()]
-        self.col_labels = [f.__name__ for f in self.feature_selectors]
-
-    def run(self, data_set):
-        data, labels = DataSets.load(data_set)
-
-        for i, feature_selector in enumerate(self.feature_selectors):
-            self.results[:, i] = self.benchmark.run(
-                data,
-                labels,
-                feature_selector.rank_data_set(data_set, self.benchmark.cv)
-            )
-
-        return self.results
-
-    def print_results(self):
-        print("DataSet Experiment: {}".format(type(self.benchmark).__name__))
-        super().print_results()
-
-
-class RawDataSetExperiment:
+class DataSetExperiment:
     root_dir = DataSets.root_dir + "/results/RAW"
 
     def __init__(self, benchmark: Benchmark, data_set_feature_selectors):
@@ -173,15 +138,15 @@ class RawDataSetExperiment:
 
     def run(self, data_sets):
         self.results = []
-        self.data_sets = data_sets
+        self.data_sets = [data_sets] if isinstance(data_sets, str) else data_sets
         bc_name = type(self.benchmark).__name__
 
-        for i, data_set in enumerate(data_sets):
+        for i, data_set in enumerate(self.data_sets):
             data, labels = DataSets.load(data_set)
             result = []
 
             for feature_selector in self.feature_selectors:
-                print("RAW {}: {} [{}]".format(
+                print("{}: {} [{}]".format(
                     bc_name,
                     data_set,
                     feature_selector.__name__
@@ -195,22 +160,25 @@ class RawDataSetExperiment:
 
             result = np.array(result)
             self.results.append(result)
-            table = Experiment.raw_results_table(
[…]

### 2016-07-28 goodness_measure.py

@@ -48,7 +48,7 @@ class GoodnessMeasure(Measure, metaclass=ABCMeta):
             goodness.append(self.goodness(
                 RankData(features_ranks[:, i].T, self.n_significant_features)
             ))
-        return goodness
+        return np.array(goodness)
 
     @abstractmethod
     def goodness(self, data: RankData):

### 2016-07-28 artificial_data.py
Bug with artificial data generation

@@ -20,10 +20,8 @@ def linear_power_labeling():
     return labeling
 
 
-def generate(n_samples, n_features, n_significant_features, feature_distribution,
-             noise_distribution=None,
-             insignificant_feature_distribution=None,
-             labeling=linear_labeling()
+def generate(n_samples, n_features, n_significant_features, feature_distribution, insignificant_feature_distribution,
+             noise_distribution=None, labeling=linear_labeling()
              ):
     if n_significant_features <= 0 or n_significant_features > n_samples:
         raise ValueError("significant needs to be positive and inferior to the number of samples")
@@ -31,13 +29,10 @@ def generate(n_samples, n_features, n_significant_features, feature_distribution
     if n_significant_features < 1:
         n_significant_features = np.ceil(n_significant_features * n_features)
 
-    if insignificant_feature_distribution is None:
-        samples = feature_distribution((n_features, n_samples))
-    else:
-        samples = np.vstack((
-            feature_distribution((n_significant_features, n_samples)),
-            insignificant_feature_distribution((n_features - n_significant_features, n_samples))
-        ))
+    samples = np.vstack((
+        feature_distribution((n_significant_features, n_samples)),
+        insignificant_feature_distribution((n_features - n_significant_features, n_samples))
+    ))
 
     if noise_distribution:
         samples += noise_distribution((n_features, n_samples))
@@ -64,23 +59,20 @@ def normal(mean, variance):
     return lambda s: np.random.normal(mean, variance, s)
 
 
-def multivariate_normal(mean, cov):
+def multivariate_normal(mean, cov, k=100):
     def distribution(s, mean=mean, cov=cov):
-        if callable(mean):
-            mean = mean(s[0])
+        m_cov = cov((s[0], s[0]))
+        # positive semi-definite matrix
+        m_cov = k * m_cov.T.dot(m_cov) / s[0]
 
-        if callable(cov):
-            cov = cov((s[0], s[0]))
-            # positive semi-definite matrix
-            cov = cov.T.dot(cov)
-
-        return np.random.multivariate_normal(mean, cov, s[1]).T
+        return np.random.multivariate_normal(mean(s[0]), m_cov, s[1]).T
 
     return distribution
 
 
 def multiple_distribution(distributions, shares):
-    def distribution(s, distributions=distributions, shares=np.array(shares)):
+    def distribution(s, distributions=distributions, shares=shares):
+        shares = np.array(list(shares))
[…]

### 2016-07-28 test.py

@@ -3,54 +3,70 @@ import ensemble_methods
 import analysis
 import artificial_data
 import numpy as np
+import matplotlib.pyplot as plt
 from data_sets import DataSets
 
 import warnings
 
 warnings.filterwarnings('ignore')
 
-# total_features = 1e4
-# n_significant_features = int(total_features*0.01)
-# DataSets.save_artificial(
-#     *artificial_data.generate(
-#         n_samples=300,
-#         n_features=total_features,
-#         n_significant_features=n_significant_features,
-#         feature_distribution=artificial_data.multivariate_normal(
-#             mean=np.zeros(n_significant_features),
-#             cov=artificial_data.uniform(-1, 1)
-#         ),
-#         insignificant_feature_distribution=artificial_data.multiple_distribution(
-#             distributions=[artificial_data.uniform(-1, 1), artificial_data.normal(0, 1)],
-#             shares=[0.5, 0.5]
-#         ),
-#         noise_distribution=artificial_data.normal(0, 0.05),
-#         labeling=artificial_data.linear_labeling(weights=np.ones(n_significant_features))
-#     )
-# )
+total_features = 1e3
+n_significant_features = 100
+DataSets.save_artificial(
+    *artificial_data.generate(
+        n_samples=300,
+        n_features=total_features,
+        n_significant_features=n_significant_features,
+        feature_distribution=artificial_data.multiple_distribution(
+            distributions=[
+                artificial_data.multivariate_normal(
+                    mean=artificial_data.constant(0),
+                    cov=artificial_data.uniform(0, 1)
+                ),
+                artificial_data.normal(0, 1)
+            ],
+            shares=[0.5, 0.5]
+        ),
+        insignificant_feature_distribution=artificial_data.multiple_distribution(
+            distributions=[
+                artificial_data.multivariate_normal(
+                    mean=artificial_data.constant(0),
+                    cov=artificial_data.uniform(0, 1)
+                ),
+                artificial_data.normal(0, 1)
+            ],
+            shares=[0.5, 0.5]
+        ),
+        labeling=artificial_data.linear_labeling(weights=np.ones(n_significant_features))
+    )
+)
 
-feature_selectors = [
[…]

### 2016-07-31 paper/paper.tex
paper rework

@@
 Used in Machine Learning and Statistics, ensemble methods combine multiple algorithms in order to obtain better performance.
-We build on the work of \cite{saeys2008} who applied ensemble learning by using the same feature selector on different subsets.
-In this work we investigate the effect of ensemble methods further by combining different feature selection methods.
+The bagging method, which consists of using the same algorithm on multiple subsets, has already been studied \cite{saeys2008}.
+The method improved considerably the robustness of the feature selection algorithm and the model performance was not significantly degraded in most cases.
+The purpose of this paper is to investigate the effect of ensemble methods further by combining different feature selection methods.
 
@@
 
-Symmetrical Uncertainty \citep{press1996numerical} is entropy based measurement. It is the normalized mutual information between the feature
-and the class. The mutual information measures the influence of the knowledge of the class on the feature value
-in terms of entropy and normalizes it. More details about mutual information can be found in \cite{paninski2003estimation}.
+Symmetrical Uncertainty \citep{press1996numerical} is entropy based measurement.
+It is the normalized mutual information between the feature and the class.
+The mutual information measures the influence of the knowledge of the class on the feature value in terms of entropy and normalizes it.
+More details about mutual information can be found in \cite{paninski2003estimation}.
 \begin{equation}
@@
 
-The second feature selection method we used is RELIEF \citep{kira1992feature}. In the beginning the weights are initialize
-with a $0$ weight.
-It then iteratively takes a random sample $x_i$ and compares it to their nearest neighboring sample belonging to their class
-$\textrm{Near-hit}_i$ and the opposite one $\textrm{Near-miss}_i$ in terms of a similarity measurement.
-The weights are set by how well these two similarity measurements distinguish as it can be seen in equation \ref{eq:relief}.
+The second feature selection is RELIEFF \citep{kononenko1997overcoming}.
+For each sample $x_i$ the k nearest neighboring samples, using the $L_1$ norm, belonging the same class $\{\textrm{Near-hit}_{i, j}\}_{j=1..k}$ and the ones of the opposite class $\{\textrm{Near-miss}_{i, j}\}_{j=1..k}$ are selected.
+Then the difference is taken to update the weight vector representing how well each feature distinguishes samples of the two classes, as can be seen in equation \ref{eq:relief}.
+In all the experiments k was set to 5, which, empirically, gives satisfactory results.
+\\
+?? \\
 In the standard case of RELIEF for comparisment the euclidean distance is used for numerical values. This inherits the
 assumption that features which are nearer to each other are also more similar, which should not be correct in each application
-area.
+area.\\
+??
 \begin{equation}
   \label{eq:relief}
-  W_i = W_i - \|x_i - \textrm{Near-hit}_i\|_2^2 + \|x_i - \textrm{Near-miss}_i\|_2^2
+  W_i = W_i - \sum_{j=1}^{k}|x_i - \textrm{Near-hit}_{i,j}| + \sum_{j=1}^{k} |x_i - \textrm{Near-miss}_{i,j}|
 \end{equation}
 
-The third feature selection method we used was a recursive feature elmination in combination with SVM \citep{guyon2002gene}.
-Recursive feature elimination fits a SVM and ranks the feature according to their importance in the model,
-based on the weight vector of the hyperplane.
-More precisely after obtaining the solution for the primal problem of the SVM in equation \ref{eq:svm_primal},
-the ranking coefficients $c_i$ for the features are then calculated by squaring the weights $c_i = w_i^2$.
+The third feature selection method used is a recursive feature elimination (RFE) with SVM \citep{guyon2002gene}.
+Recursive feature elimination fits a classifier and ranks the feature according to their importance in the model.
+In the case of the SVM, it is based on the weight vector of the hyperplane.
+More precisely after obtaining the solution for the primal problem of the SVM in equation \ref{eq:svm_primal}, the ranking coefficients $c_i$ for the features are then calculated by squaring the weights $c_i = w_i^2$.
 \begin{alignat}{-1}
@@
 The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left.
-In our case we discarded each step $10\%$ of the size of all features of the features being left. This means that
-in each step we discarded the same amount of features. This procedure was repeated until a subset of the size
-of $1\%$ of all features was left.
+In the experiments, $10\%$ of the size of all the remaining features were discarded at each step.
+This means that.
+The procedure was repeated until a subset of the size of $1\%$ of all features was left.
 
-A form of Lasso
+The last feature feature selection method used is a RFE with Lasso.
 
@@
 
-Different feature selection methods are combined by aggregating the weight they give for each feature regarding importance.
+The different feature selection methods give as output a weight vector representing how well each feature distinguishes samples of the two classes.
+The ensemble method used aggregates the different weights vectors.
 Since different methods do not always have the same weight range, they are normalized to the range $[0,1]$.
@@
 \begin{align}
-\text{significant} \quad & f \sim N(0, \Sigma) \quad \text{with} \quad \Sigma_{ij} \sim U(-1,1) \\
-\text{unsignificant} \quad & f \sim 0.5 * \left[ N(0, 1) + U(-1,1) \right]
+f \sim0.5 * \left[ N(0, 1) + N(0, \Sigma) \right]  \quad \text{with} \quad \Sigma_{ij} \sim U(0,1)
 \end{align}
+% \text{unsignificant} \quad & f \sim 0.5 * \left[ N(0, 1) + U(-1,1) \right]
 

### 2016-07-31 ensemble_methods.py
typo

@@ -24,6 +24,11 @@ class EnsembleMethod(DataSetFeatureSelector, metaclass=ABCMeta):
 
         self.feature_selectors = data_set_feature_selectors
 
+        self.__name__ += " ({})".format(self.fs_short_names())
+
+    def fs_short_names(self):
+        return "|".join(str(f) for f in self.feature_selectors)
+
     def rank_data_set(self, data_set, cv_generator):
         super().rank_data_set(data_set, cv_generator)
         bench_features_selection = []
@@ -83,13 +88,8 @@ class InfluenceStd(EnsembleMethod):
 
 
 class Mean(EnsembleMethod):
-    def __init__(self, feature_selectors, power=1):
-        super().__init__(feature_selectors)
-        self.__name__ = "Mean - {}".format(power)
-        self.power = power
-
     def combine(self, features_selection, data, labels):
-        return np.power(features_selection, self.power).mean(axis=0)
+        return features_selection.mean(axis=0)
 
 
 class MeanStd(EnsembleMethod):
@@ -99,7 +99,6 @@ class MeanStd(EnsembleMethod):
         self.power = power
 
     def combine(self, features_selection, data, labels):
-        influence = (features_selection.T / features_selection.sum(axis=1)).T
         return np.power(features_selection, self.power).mean(axis=0) / features_selection.std(axis=0)
 
 
@@ -107,7 +106,7 @@ class SMean(EnsembleMethod):
     def __init__(self, feature_selectors, min_mean_max=[1, 1, 1]):
         super().__init__(feature_selectors)
         self.weights = np.array(min_mean_max)
-        self.__name__ = "SMean - {} {} {}".format(*min_mean_max)
+        self.__name__ = "SMean - {} {} {} ({})".format(*min_mean_max, self.fs_short_names())
 
     def combine(self, features_selection, data, labels):
         f_mean = np.mean(features_selection, axis=0)
@@ -116,11 +115,9 @@ class SMean(EnsembleMethod):
         return (np.vstack((f_min, f_mean, f_max)) * self.weights[:, np.newaxis]).mean(axis=0)
 
 
-class SMeanWithClassifier(EnsembleMethod):
-    def __init__(self, feature_selectors, classifiers, min_mean_max=[1, 1, 1], **kwargs):
-        super().__init__(feature_selectors, **kwargs)
-        self.weights = np.array(min_mean_max)
[…]

### 2016-07-31 feature_selector.py

@@ -130,6 +130,9 @@ class FeatureSelector(DataSetFeatureSelector, metaclass=ABCMeta):
         mkdir(PreComputedData.dir_name(data_set, cv, method))
         np.save(PreComputedData.file_name(data_set, cv, method, self), feature_selection)
 
+    def __str__(self):
+        return "FS"
+
 
 class DummyFeatureSelector(FeatureSelector):
     def rank(self, data, labels):
@@ -149,12 +152,18 @@ class SymmetricalUncertainty(FeatureSelector):
             )
         return self.normalize(np.array(features_weight))
 
+    def __str__(self):
+        return "SU"
+
 
 class Relief(FeatureSelector):
     def weight(self, data, labels):
         features_weight = skfeature.function.similarity_based.reliefF.reliefF(data.T, labels)
 
         return self.normalize(features_weight)
+
+    def __str__(self):
+        return "RLF"
 
 
 class SVM_RFE(FeatureSelector):
@@ -182,12 +191,18 @@ class SVM_RFE(FeatureSelector):
     def reverse_order(ranks):
         return -ranks + np.max(ranks) + 1
 
+    def __str__(self):
+        return "SVM"
+
 
 class LassoFeatureSelector(FeatureSelector):
     def weight(self, data, labels):
         lasso = LogisticRegressionCV(penalty='l1', solver='liblinear')
         lasso.fit(data.T, labels)
         return self.normalize(np.abs(lasso.coef_[0]))
+
+    def __str__(self):
+        return "LSO"
 
 
 class Random(FeatureSelector):

### 2016-08-01 test.py
test

@@ -5,68 +5,144 @@ import artificial_data
 import numpy as np
 import matplotlib.pyplot as plt
 from data_sets import DataSets
+import itertools
+from experiments import Experiment
 
 import warnings
 
 warnings.filterwarnings('ignore')
 
-total_features = 1e3
-n_significant_features = 100
-DataSets.save_artificial(
-    *artificial_data.generate(
-        n_samples=300,
-        n_features=total_features,
-        n_significant_features=n_significant_features,
-        feature_distribution=artificial_data.multiple_distribution(
-            distributions=[
-                artificial_data.multivariate_normal(
-                    mean=artificial_data.constant(0),
-                    cov=artificial_data.uniform(0, 1)
-                ),
-                artificial_data.normal(0, 1)
-            ],
-            shares=[0.5, 0.5]
-        ),
-        insignificant_feature_distribution=artificial_data.multiple_distribution(
-            distributions=[
-                artificial_data.multivariate_normal(
-                    mean=artificial_data.constant(0),
-                    cov=artificial_data.uniform(0, 1)
-                ),
-                artificial_data.normal(0, 1)
-            ],
-            shares=[0.5, 0.5]
-        ),
-        labeling=artificial_data.linear_labeling(weights=np.ones(n_significant_features))
-    )
-)
+# total_features = 1e4
+# n_significant_features = 100
+# DataSets.save_artificial(
+#     *artificial_data.generate(
+#         n_samples=300,
+#         n_features=total_features,
+#         n_significant_features=n_significant_features,
+#         feature_distribution=artificial_data.multiple_distribution(
+#             distributions=[
+#                 artificial_data.multivariate_normal(
+#                     mean=artificial_data.constant(0),
+#                     cov=artificial_data.uniform(0, 1)
+#                 ),
+#                 artificial_data.normal(-1, 1)
+#             ],
+#             shares=[0.5, 0.5]
+#         ),
+#         insignificant_feature_distribution=artificial_data.multiple_distribution(
+#             distributions=[
[…]

### 2016-08-01 ensemble_methods.py
Influence with arctanh DataSetExperiment with mean

@@ -75,8 +75,13 @@ class EnsembleMethod(DataSetFeatureSelector, metaclass=ABCMeta):
 
 
 class Influence(EnsembleMethod):
+    def __init__(self, fs, k=1):
+        super().__init__(fs)
+        self.k = k
+        self.__name__ += " - {}".format(k)
+
     def combine(self, feature_selection, data, labels):
-        feature_selection = np.exp(feature_selection)
+        feature_selection = np.exp(np.arctanh(self.k * (feature_selection - 1)))
         return (feature_selection.T / feature_selection.sum(axis=1)).T.mean(axis=0)
 
 

### 2016-08-01 paper/paper.tex
typo
experiment rework

@@
   \label{eq:relief}
-  W_i = W_i - \sum_{j=1}^{k}|x_i - \textrm{Near-hit}_{i,j}| + \sum_{j=1}^{k} |x_i - \textrm{Near-miss}_{i,j}|
+  W_i = W_i - \frac{1}{k}\sum_{j=1}^{k}|x_i - \textrm{Near-hit}_{i,j}| + \frac{1}{k}\sum_{j=1}^{k} |x_i - \textrm{Near-miss}_{i,j}|
 \end{equation}
@@
 
+Ensemble
+
 The different feature selection methods give as output a weight vector representing how well each feature distinguishes samples of the two classes.
-The ensemble method used aggregates the different weights vectors.
+Those are then be combined by the ensemble method.
 Since different methods do not always have the same weight range, they are normalized to the range $[0,1]$.
@@
 
+Furthermore, different combinations of feature selectors were used in order to find combinations which work better than others.
+
 \section{Evaluation}
 
-While the purpose of this paper is to find a robust feature selection method, it is also necessary to evaluate the classification performance as domain export have no interest in badly performing model.
-Hence those two aspects are always considered in combination
+While the purpose of this paper is to find a robust feature selection method, it is also necessary to evaluate the classification performance as domain expert have no interest in badly performing model.
+Hence those two aspects are always considered in combination.
 
@@
 Datasets are taken from the NIPS 2003 challenge \cite{NIPS}.
-However, due to computation power constraints not the whole dataset is always used.
+However, due to computation power constraints, not the whole dataset is always used.
 Additionally the colon data set \cite{alon1999broad} is used.
@@
 
-The robustness is evaluated with a ShuffleSplit of 10 folds with 90\% of the data, as the number of samples is already limited.
-After weighting the features the best ones are taken (from 0.1\% to 1\%) and those subsets are compared with the Jaccard Index.
+Feature selectors needs to be robust but also accurate, therefore both model performance and robustness were measured.
+
+The model performance is estimated by measuring the balanced error rate of a set of classifiers: Lasso, linear SVM, k-nearest neighbor, Random Forest.
+For each classifier the performance was assessed using a 10-fold cross validation setting and trained on the best 1\% of the data.
+
+To measure the robustness, different equally sized subsamples are drawn from the dataset.
+The feature selector runs on all of them, and the best ones are taken based.
+The subsets are then compared with a similarity measure.
+Given that the model performance is measured on the best 1\% of the features, the order of the feature should not be of importance but only if one is or not part of the best subset.
+Hence the Jaccard Index was used because only how many features are common to both sets is important for this measure.
 For two subsets of features $F_i$ and $F_j$ it is defined as:
@@
 \end{equation}
-
-The classification performance is estimated with a cross validation of 10 folds with multiple classifiers, trained and tested on the subset of features.
-4 different classifiers are used: Lasso, linear SVM, k-nearest neighbor, Random Forest.
 

### 2016-08-02 paper/paper.tex
FS updated, sklearn citation added at appendix

--- 2016-07-31 paper/paper.tex
@@
 In all the experiments k was set to 5, which, empirically, gives satisfactory results.
-\\
-?? \\
-In the standard case of RELIEF for comparisment the euclidean distance is used for numerical values. This inherits the
-assumption that features which are nearer to each other are also more similar, which should not be correct in each application
-area.\\
-??
 \begin{equation}
   \label{eq:relief}
-  W_i = W_i - \sum_{j=1}^{k}|x_i - \textrm{Near-hit}_{i,j}| + \sum_{j=1}^{k} |x_i - \textrm{Near-miss}_{i,j}|
+  W_i = W_i - \frac{1}{k}\sum_{j=1}^{k}|x_i - \textrm{Near-hit}_{i,j}| + \frac{1}{k}\sum_{j=1}^{k} |x_i - \textrm{Near-miss}_{i,j}|
 \end{equation}
@@
 The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left.
-In the experiments, $10\%$ of the size of all the remaining features were discarded at each step.
-This means that.
+In the experiments, $10\%$ of the size of all features were discarded at each step.
 The procedure was repeated until a subset of the size of $1\%$ of all features was left.
+Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps.
+Therefore a SVM is $10$ times needed to be evaluated.
+Another method would be to discard only $10\%$ of the remaining features.
+A more gradually ascend of feature weights can be achievedthis way.
+However this was not computable with our ressources.
+For the hpyerparameter $C$ a grid search on the set $/{1, 10, 100, 1000\}$ was done.
+The parameters were evaluated with stratisfied 5-fold cross-validation.
 
-The last feature feature selection method used is a RFE with Lasso.
+The last feature selection method used is Lasso logistc regression \citep{wheeler2010lasso}.
+It is a logistic regression with a $L_1$ norm as penalty for the weight vector.
+For the hyperparameter $C$ a grid search with $10$ different parameters in logarithmic scale between $10^{-5}$ and $10^3$ was done.
+The parameters were evaluated with a stratisfied 3-fold cross-validation.
 
 \begin{equation}
-  \min_w \quad \frac1{2 \, \textrm{\#features}} \, \|y - Xw\|^2_2 + \alpha \, \|w\|_1
+  \min_{w,c} \quad \|w\|_1 + C\sum_{i=1}^n \log(\exp(y_i(x_i^Tw + c))+1)
 \end{equation}
 
+The advantage of this method is that we obtain a sparse weight vector as solution. This means only a small subset of features will have a significant high weight.
 \section{Ensemble methods}
@@
 The classification performance is estimated with a cross validation of 10 folds with multiple classifiers, trained and tested on the subset of features.
-4 different classifiers are used: Lasso, linear SVM, k-nearest neighbor, Random Forest.
+4 different classifiers are used: Lasso logistic regression, linear SVM, k-nearest neighbor, Random Forest.
 
@@
 \section*{Appendix A.}
-For the feature selection methods SU and RELIEF e used the scikit-feature library from \cite{Li-etal16}.
+For the feature selection methods SU and RELIEFF we used the scikit-feature library from \cite{Li-etal16}.
+For SVM, RFE, Lasso logistic regression we used the scikit-sklearn library from \cite{scikit-learn}
 \label{app:some appendix}

### 2016-08-02 paper/paper.tex
removed merge comments

@@
 However this was not computable with our ressources.
-For the hpyerparameter $C$ a grid search on the set $/{1, 10, 100, 1000\}$ was done.
+For the hpyerparameter $C$ a grid search on the set $\{1, 10, 100, 1000\}$ was done.
 The parameters were evaluated with stratisfied 5-fold cross-validation.
@@
 \subsection{Results}
-- Do SVM\_RFE with exponential rising
 - SU achieved high values in the paper, in our results SU weighted a lot of features the 
@@
 robustness by order of features
-- The noise features of the NIPS 2003 challenge data sets are highly correlated with the
-real feature; therefore no improvement has been made with feature selection in terms of 
-accuracy
+
 % Acknowledgements should go at the end, before appendices and references

### 2016-08-02 paper/paper.tex
robustness of the different combinations

--- 2016-08-01 paper/paper.tex
@@
 
-Symmetrical Uncertainty \citep{press1996numerical} is entropy based measurement.
+Symmetrical Uncertainty (SU) \citep{press1996numerical} is entropy based measurement.
 It is the normalized mutual information between the feature and the class.
@@
 \begin{description}[align=left]
-\item [Linear aggregation :] The average of the weights was taken as the new weight.
-\item [Non-linear aggregation :] Two methods were used, first averaging powers of the weights and secondly aggregating linearly the minimum, maximum and the average of the weights.
+\item [Linear aggregation :] The average of the weights was taken as the new weight. Two version were used, one where a normalization of the weight sum is applied and the other without it.
+\item [Non-linear aggregation :] To emphasize features with importance, the weights are non-linearly transformed with the equation \ref{eq:em_non_linear}.
+$\arctan$ in in combination with $\exp$ to considerably shrink the low weights.
+Finally the weights sum is normalized.
+
+\begin{equation}
+  \label{eq:em_non_linear}
+  W_i = \frac{f \left( W_i \right)}{\sum_k f \left( W_k \right)} \quad with \quad f : x \rightarrow \exp( \arctan(x - 1) )
+\end{equation}
+
 \item [Performance related aggregation :] For each feature selector the best 1\% of the features were selected and used to measure the classification performance for multiple classifiers.
 The feature selection methods result were weighted accordingly to their accuracy.
+It was used in combination with the precedent ensemble methods.
 \end{description}
@@
 
+\subsubsection{Different combinations of feature selectors}
+The presented ensemble methods were used with all possible combinations of feature selectors.
+For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
+While the accuracy does not change considerably with the different combinations, the robustness is heavily affected by the presence or not of the feature selector Lasso as can be seen in the figure \ref{fig:combination_robustness}.
+This is due to the low robustness of the feature selector Lasso itself.
+On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.
+
+\begin{figure}
+\centering \includegraphics[]{images/Robustness_of_the_different_combinations.pdf}
+\caption{Robustness of the different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
+\label{fig:combination_robustness}
+\end{figure}
+
 \newpage

### 2016-08-02 paper/paper.tex
combination_accuracy figure

@@
 \usepackage{enumitem}
+\usepackage{subcaption}
 
@@
 In all the experiments k was set to 5, which, empirically, gives satisfactory results.
-\\
-?? \\
-In the standard case of RELIEF for comparisment the euclidean distance is used for numerical values. This inherits the
-assumption that features which are nearer to each other are also more similar, which should not be correct in each application
-area.\\
-??
 \begin{equation}
@@
 \subsection{Data Sets}
-Datasets are taken from the NIPS 2003 challenge \cite{NIPS}.
+Datasets are taken from the NIPS 2003 challenge (\cite{NIPS}).
 However, due to computation power constraints, not the whole dataset is always used.
-Additionally the colon data set \cite{alon1999broad} is used.
+Additionally the colon data set (\cite{alon1999broad}) is used.
 Finally artificial data is also generated, since it is possible to control which features are meaningful.
@@
 For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
-While the accuracy does not change considerably with the different combinations, the robustness is heavily affected by the presence or not of the feature selector Lasso as can be seen in the figure \ref{fig:combination_robustness}.
+While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or not of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}.
 This is due to the low robustness of the feature selector Lasso itself.
@@
 \begin{figure}
-\centering \includegraphics[]{images/Robustness_of_the_different_combinations.pdf}
-\caption{Robustness of the different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
+  \caption{Accuracy}
+  \label{fig:combination_accuracy}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
+  \caption{Robustness}
   \label{fig:combination_robustness}
+\end{subfigure}
+\caption{Different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
+\label{fig:combination_results}
 \end{figure}

### 2016-08-02 paper/paper.tex
comparison of methods

@@
 
-\begin{figure}
+The methods were also compared with regards to their performance and robustness on the different combinations.
+However, as can be seen in figure \ref{fig:methods_results} the methods do not seems to have a great impact on the results.
+Therefore the choice of the combined feature selectors appears to be more important than the methods used to combine them.
+
+\begin{figure}[!t]
 \centering
@@
 \end{subfigure}
-\caption{Different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
+\caption{Results for the different combination of feature selectors. RLF and LSO corresponds respectively to RELIEFF and Lasso.}
 \label{fig:combination_results}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_methods.pdf}
+  \caption{Accuracy}
+  \label{fig:methods_accuracy}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_methods.pdf}
+  \caption{Robustness}
+  \label{fig:methods_robustness}
+\end{subfigure}
+\caption{Results for the different methods on average on the different combinations.
+"Average +" is the average method with the normalized sum.
+When "\& Perf." is indicated the performance was also used to aggregate the weights.}
+\label{fig:methods_results}
 \end{figure}

### 2016-08-02 paper/paper.tex
Added analyse about artificial data, and FS distribution

--- 2016-08-02 paper/paper.tex
@@
 
-Symmetrical Uncertainty (SU) \citep{press1996numerical} is entropy based measurement.
+Symmetrical Uncertainty \citep{press1996numerical} is entropy based measurement.
 It is the normalized mutual information between the feature and the class.
@@
 The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left.
-In the experiments, $10\%$ of the size of all the remaining features were discarded at each step.
-This means that.
+In the experiments, $10\%$ of the size of all features were discarded at each step.
 The procedure was repeated until a subset of the size of $1\%$ of all features was left.
+Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps.
+Therefore a SVM is $10$ times needed to be evaluated.
+Another method would be to discard only $10\%$ of the remaining features.
+A more gradually ascend of feature weights can be achievedthis way.
+However this was not computable with our ressources.
+For the hpyerparameter $C$ a grid search on the set $\{1, 10, 100, 1000\}$ was done.
+The parameters were evaluated with stratisfied 5-fold cross-validation.
 
-The last feature feature selection method used is a RFE with Lasso.
+The last feature selection method used is Lasso logistc regression \citep{wheeler2010lasso}.
+It is a logistic regression with a $L_1$ norm as penalty for the weight vector.
+For the hyperparameter $C$ a grid search with $10$ different parameters in logarithmic scale between $10^{-5}$ and $10^3$ was done.
+The parameters were evaluated with a stratisfied 3-fold cross-validation.
 
 \begin{equation}
-  \min_w \quad \frac1{2 \, \textrm{\#features}} \, \|y - Xw\|^2_2 + \alpha \, \|w\|_1
+  \min_{w,c} \quad \|w\|_1 + C\sum_{i=1}^n \log(\exp(y_i(x_i^Tw + c))+1)
 \end{equation}
 
+The advantage of this method is that we obtain a sparse weight vector as solution. This means only a small subset of features will have a significant high weight.
 \section{Ensemble methods}
@@
 \begin{description}[align=left]
-\item [Linear aggregation :] The average of the weights was taken as the new weight. Two version were used, one where a normalization of the weight sum is applied and the other without it.
-\item [Non-linear aggregation :] To emphasize features with importance, the weights are non-linearly transformed with the equation \ref{eq:em_non_linear}.
-$\arctan$ in in combination with $\exp$ to considerably shrink the low weights.
-Finally the weights sum is normalized.
-
-\begin{equation}
-  \label{eq:em_non_linear}
-  W_i = \frac{f \left( W_i \right)}{\sum_k f \left( W_k \right)} \quad with \quad f : x \rightarrow \exp( \arctan(x - 1) )
-\end{equation}
-
+\item [Linear aggregation :] The average of the weights was taken as the new weight.
+\item [Non-linear aggregation :] Two methods were used, first averaging powers of the weights and secondly aggregating linearly the minimum, maximum and the average of the weights.
 \item [Performance related aggregation :] For each feature selector the best 1\% of the features were selected and used to measure the classification performance for multiple classifiers.
 The feature selection methods result were weighted accordingly to their accuracy.
-It was used in combination with the precedent ensemble methods.
 \end{description}
@@
 
+The classification performance is estimated with a cross validation of 10 folds with multiple classifiers, trained and tested on the subset of features.
+4 different classifiers are used: Lasso logistic regression, linear SVM, k-nearest neighbor, Random Forest.
+
 \subsection{Results}
-- Do SVM\_RFE with exponential rising
 - SU achieved high values in the paper, in our results SU weighted a lot of features the 
@@
 robustness by order of features
-- The noise features of the NIPS 2003 challenge data sets are highly correlated with the
-real feature; therefore no improvement has been made with feature selection in terms of 
-accuracy
-% Acknowledgements should go at the end, before appendices and references
+
+\subsubsection{Properties of FS}
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=\textwidth]{feature_weights_hist_arcene_artificial.png}
+  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
+  \label{fig:feature_weights_hist_arcene_artificial}
+\end{figure}
+In figure \ref{fig:feature_weights_hist_arcene_artificial} the histograms of the features weight can be seen for the arcene and the artificial data set.
+It is observable that the distribution of the feature weights have similiar shapes on each data set for RELIEFF, SVM RFE, Lasso logistic regression.
+In addition the distributions are centered around the same area.
+RELIEFF and Lasso seem to always have a strong peak.
+Lasso even stronger than RELIEFF, which is an effect of the sparsity of Lasso.
+On the other hand SU varies a lot on different data sets and does not seem to have a consistent shape.
+For some data sets like the artifical data set SU mainly outputs one value for all features.
+On others like arcene it is greatly distributed.
+The histograms for all data sets can be seen in the appendix in figure \ref{fig:feature_weights_hist}.
+
+\subsubsection{Results to artificial data set}
+\begin{figure}
+  \centering 
+  \begin{subfigure}[b]{0.48\textwidth}
+      \includegraphics[width=\textwidth]{feature_weights_plot_artificial_only_features.png}
+      \caption{Features weights for the real features.}
+      \label{fig:feature_weights_plot_artificial_only_features}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{feature_weights_plot_artificial_all.png}
+      \caption{Features weights for all features.}
+      \label{fig:feature_weights_plot_artificial_all}
+  \end{subfigure}
+
+  \caption{The features weights for once for only the real features and once for all.
+In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the real multivariate features and in the cyan area are the real univariate features.
+In figure \ref{fig:feature_weights_plot_artificial_all} in the green are all real features, in the red area are the fake multivariate features and in the orange area are the fake univariate features.
+}
+  \label{fig:feature_weights_plot_artificial}
+\end{figure}
+\begin{figure}[h!]
+  \centering
+  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
+\end{figure}
+The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
+All feature selectors achieved similar results for the artificial data set except of SU.
+SU does not rank iall features with a zero weight which makes SU fully random on this data set.
+On the contrary the other feature selectors recognize parts of the inherent structure of the data.
+The univariate features are in general ranked lower than the multivariate features.
+There seems to be no diffierence in weighting between the real und fake univariate features.
+However the real multivariate features are ranked significantly higher than the fake multivariate features.
+As a consequence only multivariate features are selected.
+The reason why the feature selectors weight the real univariate features this low is that the univariate features do not contribute significantly to the classification.
+If we use only the real multivariate features with the same classification function with which the labels were created, we achieve an accuracy of $0.98$.
+On the other hand using the real univariate features we only achieve an accuracy of $0.52$.
+Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
+Furthermore the feature seletors were evaluated after how many real features they capture in the $100$ the highest weighted features.
+RELIEFF achieved the highest precision of $0.5$, SVM RFE achieved $0.48$, then Lasso with $0.24$ and SU with $0$.
 
@@
 
-\subsubsection{Different combinations of feature selectors}
-The presented ensemble methods were used with all possible combinations of feature selectors.
-For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
-While the accuracy does not change considerably with the different combinations, the robustness is heavily affected by the presence or not of the feature selector Lasso as can be seen in the figure \ref{fig:combination_robustness}.
-This is due to the low robustness of the feature selector Lasso itself.
-On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.
-
-\begin{figure}
-\centering \includegraphics[]{images/Robustness_of_the_different_combinations.pdf}
-\caption{Robustness of the different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
-\label{fig:combination_robustness}
-\end{figure}
-
 \newpage
@@
 \section*{Appendix A.}
-For the feature selection methods SU and RELIEF e used the scikit-feature library from \cite{Li-etal16}.
-\label{app:some appendix}
+For the feature selection methods SU and RELIEFF we used the scikit-feature library from \cite{Li-etal16}.
+For SVM, RFE, Lasso logistic regression we used the scikit-sklearn library from \cite{scikit-learn}
+\label{app:appendixa}
+\section*{Appendix B.}
+\label{app:appendixb}
 
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=\textwidth]{feature_weights_hist.png}
+  \caption{The histogram of the feature weights for all feature selectors used for all data sets used.}
+  \label{fig:feature_weights_hist}
+\end{figure}
 % Note: in this sample, the section number is hard-coded in. Following

### 2016-08-02 goodness_measure.py
Precision EM

@@ -5,39 +5,41 @@ import numpy as np
 
 
 class RankData:
-    def __init__(self, features_rank, n_significant_features):
+    def __init__(self, features_rank, n_significant_features, n_indices):
         self.features_rank = features_rank
         self.sorted_indices = np.argsort(features_rank)[::-1]
         self.n_significant = n_significant_features
+        self.n_indices = n_indices
 
     def __len__(self):
         return len(self.features_rank)
 
     @property
     def true_positive(self):
-        return (self.sorted_indices[:self.n_significant] < self.n_significant).sum()
+        return (self.sorted_indices[:self.n_indices] < self.n_significant).sum()
 
     @property
     def false_positive(self):
-        return (self.sorted_indices[:self.n_significant] >= self.n_significant).sum()
+        return (self.sorted_indices[:self.n_indices] >= self.n_significant).sum()
 
     @property
     def true_negative(self):
-        return (self.sorted_indices[self.n_significant:] >= self.n_significant).sum()
+        return (self.sorted_indices[self.n_indices:] >= self.n_significant).sum()
 
     @property
     def false_negative(self):
-        return (self.sorted_indices[self.n_significant:] < self.n_significant).sum()
+        return (self.sorted_indices[self.n_indices:] < self.n_significant).sum()
 
 
 class GoodnessMeasure(Measure, metaclass=ABCMeta):
-    def __init__(self, data_set_name):
+    def __init__(self, data_set_name, n_indices=None):
         super().__init__()
         feature_probe_labels = DataSets.load_features_labels(data_set_name)
         if feature_probe_labels is None:
             self.n_significant_features = None
         else:
             self.n_significant_features = np.sum([feature_probe_labels == 1])
+        self.n_indices = self.n_significant_features if n_indices is None else n_indices
 
     def measures(self, features_ranks):
         if not self.n_significant_features:
@@ -46,7 +48,7 @@ class GoodnessMeasure(Measure, metaclass=ABCMeta):
         goodness = []
         for i in range(features_ranks.shape[1]):
             goodness.append(self.goodness(
-                RankData(features_ranks[:, i].T, self.n_significant_features)
+                RankData(features_ranks[:, i].T, self.n_significant_features, self.n_indices)
             ))
         return np.array(goodness)
 

### 2016-08-02 paper/paper.tex

--- 2016-08-02 paper/paper.tex
@@
 
-The features of the artificial dataset are generated with two distributions, depending on whether they are used in the labeling process or not.
+The features of the artificial dataset are generated with two Gaussian distributions, depending on whether they are used in the labeling process or not.
 
@@
 \end{equation}
-
-\subsection{Results}
-- Do SVM\_RFE with exponential rising
-- SU achieved high values in the paper, in our results SU weighted a lot of features the 
-same; therefore for robustness same weights have to be shuffled to not accidental increase
-robustness by order of features
-- The noise features of the NIPS 2003 challenge data sets are highly correlated with the
-real feature; therefore no improvement has been made with feature selection in terms of 
-accuracy
-% Acknowledgements should go at the end, before appendices and references
-
-%\acks{I want to thank my mum}
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\subsubsection{Different combinations of feature selectors}
-The presented ensemble methods were used with all possible combinations of feature selectors.
-For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
-While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or not of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}.
-This is due to the low robustness of the feature selector Lasso itself.
-On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.
-
-The methods were also compared with regards to their performance and robustness on the different combinations.
-However, as can be seen in figure \ref{fig:methods_results} the methods do not seems to have a great impact on the results.
-Therefore the choice of the combined feature selectors appears to be more important than the methods used to combine them.
 
@@
 
+\subsection{Results}
+In this section we present our results for the experiments
+\subsubsection{Distribution of feature selectors}
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=\textwidth]{feature_weights_hist_arcene_artificial.png}
+  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
+  \label{fig:feature_weights_hist_arcene_artificial}
+\end{figure}
+In figure \ref{fig:feature_weights_hist_arcene_artificial} the histograms of the features weight can be seen for the arcene and the artificial data set.
+It is observable that the distribution of the feature weights have similiar shapes on each data set for RELIEFF, SVM RFE, Lasso logistic regression.
+In addition the distributions are centered around the same area.
+RELIEFF and Lasso seem to always have a strong peak.
+Lasso even stronger than RELIEFF, which is an effect of the sparsity of Lasso.
+On the other hand SU varies a lot on different data sets and does not seem to have a consistent shape.
+For some data sets like the artifical data set SU mainly outputs one value for all features.
+On others like arcene it is greatly distributed.
+The histograms for all data sets can be seen in the appendix in figure \ref{fig:feature_weights_hist}.
+
+\subsubsection{Results for the artificial data set}
+\begin{figure}
+  \centering 
+  \begin{subfigure}[b]{0.48\textwidth}
+      \includegraphics[width=\textwidth]{feature_weights_plot_artificial_only_features.png}
+      \caption{Features weights for the real features.}
+      \label{fig:feature_weights_plot_artificial_only_features}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{feature_weights_plot_artificial_all.png}
+      \caption{Features weights for all features.}
+      \label{fig:feature_weights_plot_artificial_all}
+  \end{subfigure}
+
+  \caption{The features weights for once for only the real features and once for all.
+In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the real multivariate features and in the cyan area are the real univariate features.
+In figure \ref{fig:feature_weights_plot_artificial_all} in the green are all real features, in the red area are the fake multivariate features and in the orange area are the fake univariate features.
+}
+  \label{fig:feature_weights_plot_artificial}
+\end{figure}
+\begin{figure}[h!]
+  \centering
+  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
+\end{figure}
+The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
+All feature selectors achieved similar results for the artificial data set except of SU.
+SU does not rank iall features with a zero weight which makes SU fully random on this data set.
+On the contrary the other feature selectors recognize parts of the inherent structure of the data.
+The univariate features are in general ranked lower than the multivariate features.
+There seems to be no diffierence in weighting between the real und fake univariate features.
+However the real multivariate features are ranked significantly higher than the fake multivariate features.
+As a consequence only multivariate features are selected.
+The reason why the feature selectors weight the real univariate features this low is that the univariate features do not contribute significantly to the classification.
+If we use only the real multivariate features with the same classification function with which the labels were created, we achieve an accuracy of $0.98$.
+On the other hand using the real univariate features we only achieve an accuracy of $0.52$.
+Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
+Furthermore the feature seletors were evaluated after how many real features they capture in the $100$ the highest weighted features.
+RELIEFF achieved the highest precision of $0.5$, SVM RFE achieved $0.48$, then Lasso with $0.24$ and SU with $0$.
+% Acknowledgements should go at the end, before appendices and references
+
+%\acks{I want to thank my mum}
+
+% Manual newpage inserted to improve layout of sample file - not
+% needed in general before appendices/bibliography.
+
+\subsubsection{Different combinations of feature selectors}
+The presented ensemble methods were used with all possible combinations of feature selectors.
+For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
+While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or not of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}.
+This is due to the low robustness of the feature selector Lasso itself.
+On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.
+
+The methods were also compared with regards to their performance and robustness on the different combinations.
+However, as can be seen in figure \ref{fig:methods_results} the methods do not seems to have a great impact on the results.
+Therefore the choice of the combined feature selectors appears to be more important than the methods used to combine them.
+
+\vskip 0.2in
+\bibliography{references}
+
 \newpage
@@
 \section*{Appendix A.}
-For the feature selection methods SU and RELIEF e used the scikit-feature library from \cite{Li-etal16}.
-\label{app:some appendix}
+For the feature selection methods SU and RELIEFF we used the scikit-feature library from \cite{Li-etal16}.
+For SVM, RFE, Lasso logistic regression we used the scikit-sklearn library from \cite{scikit-learn}
+\label{app:appendixa}
+\section*{Appendix B.}
+\label{app:appendixb}
+
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=\textwidth]{feature_weights_hist.png}
+  \caption{The histogram of the feature weights for all feature selectors used for all data sets used.}
+  \label{fig:feature_weights_hist}
+\end{figure}
 
@@
 
-\vskip 0.2in
-\bibliography{references}
-
 \end{document}

### 2016-08-03 paper/paper.tex
on figure too much, replaced combinations
boxplot addded

@@
 \usepackage{subcaption}
-
+\usepackage{float}
 % Definitions of handy macros can go here
@@
 
-\begin{figure}[!t]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
-  \caption{Accuracy}
-  \label{fig:combination_accuracy}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
-  \caption{Robustness}
-  \label{fig:combination_robustness}
-\end{subfigure}
-\caption{Results for the different combination of feature selectors. RLF and LSO corresponds respectively to RELIEFF and Lasso.}
-\label{fig:combination_results}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_methods.pdf}
-  \caption{Accuracy}
-  \label{fig:methods_accuracy}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_methods.pdf}
-  \caption{Robustness}
-  \label{fig:methods_robustness}
-\end{subfigure}
-\caption{Results for the different methods on average on the different combinations.
-"Average +" is the average method with the normalized sum.
-When "\& Perf." is indicated the performance was also used to aggregate the weights.}
-\label{fig:methods_results}
-\end{figure}
-
 \subsection{Results}
@@
 
-  \caption{The features weights for once for only the real features and once for all.
+  \caption{The features weights  once for only the real features and once for all.
 In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the real multivariate features and in the cyan area are the real univariate features.
@@
   \label{fig:feature_weights_plot_artificial}
-\end{figure}
-\begin{figure}[h!]
-  \centering
-  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
 \end{figure}
@@
 
+\begin{figure}[!b]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
+  \caption{Accuracy}
+  \label{fig:combination_accuracy}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
+  \caption{Robustness}
+  \label{fig:combination_robustness}
+\end{subfigure}
+\caption{Results for the different combination of feature selectors. RLF and LSO corresponds respectively to RELIEFF and Lasso.}
+\label{fig:combination_results}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_methods.pdf}
+  \caption{Accuracy}
+  \label{fig:methods_accuracy}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_methods.pdf}
+  \caption{Robustness}
+  \label{fig:methods_robustness}
+\end{subfigure}
+\caption{Results for the different methods on average on the different combinations.
+"Average +" is the average method with the normalized sum.
+When "\& Perf." is indicated the performance was also used to aggregate the weights.}
+\label{fig:methods_results}
+\end{figure}
+
+\subsubsection{Ensemble methods in comparisment to single feature selection}
+
+As we can see in figure \ref{fig:boxplot} the ensemble methods achieve good results on each data set.
+While single feature selection methods achieve better results in terms of accuracy and robustness on some data sets, they fail on others.
+The ensemble methods hold their performance for each dataset.
+On the arcene data set they even achive better results than any single feature selector.
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=\textwidth]{images/boxplot.pdf}
+  \caption{The different ensemble methods compared with single feature selectors in comparisment of stability and accuracy.
+  The gray area is the accuracy when using no feature selection.}
+  \label{fig:boxplot}
+\end{figure}
+
+\section{Discussion}
+We have shown that ensemble methods can hold on to results of single feauter selectors and are even superior to the tested feature selectors in terms of generality on different data sets.
+Further knowledge about the weakness and strength of certain feature selectors can exploited to create good ensembles of feature selectors.
+It it also has to be tested if the ensemble methods we tried in this work, will also work on other data sets.
+
 \vskip 0.2in

### 2016-08-04 paper/paper.tex
added info to artificial dataset, added library info, std info of boxplots

--- 2016-08-02 paper/paper.tex
@@
 \usepackage{subcaption}
+\usepackage{float}
+\usepackage{cleveref}
+\usepackage{hyperref}
 
@@
 \title{Ensemble Methods for Robust Feature Selection}
-
+%TODO write C-SVM and not SVM
+%TODO check if it is written that same weights are ranked random
 \author{\name Benjamin Rapier \email benjamin.rabier@campus.tu-berlin.de \\
@@
 
-Feature selection is a preprocessing step used in machine learning application to find a small subset of features in order to build a more accurate, simpler and faster model.
+Feature selection is a method used in machine learning to find a small subset of features in order to build a more accurate, simpler and faster model.
+It is often used with high dimensional data.
 Moreover it allows domain experts to gain a better understanding of the data, by focusing on the selected subset.
@@
 Used in Machine Learning and Statistics, ensemble methods combine multiple algorithms in order to obtain better performance.
-The bagging method, which consists of using the same algorithm on multiple subsets, has already been studied \cite{saeys2008}.
-The method improved considerably the robustness of the feature selection algorithm and the model performance was not significantly degraded in most cases.
+The bagging method, which consists of using the same algorithm on multiple subsets, has already been studied in \cite{saeys2008}.
+The method improved considerably the robustness of the feature selection algorithm while the model performance was not significantly degraded in most cases.
 The purpose of this paper is to investigate the effect of ensemble methods further by combining different feature selection methods.
@@
 The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left.
-In the experiments, $10\%$ of the size of all the remaining features were discarded at each step.
-This means that.
+In the experiments, $10\%$ of the size of all features were discarded at each step.
 The procedure was repeated until a subset of the size of $1\%$ of all features was left.
+Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps.
+Therefore a SVM is $10$ times needed to be evaluated.
+Another method would be to discard only $10\%$ of the remaining features.
+A more gradually ascend of feature weights can be achievedthis way.
+However this was not computable with our ressources.
+For the hpyerparameter $C$ a grid search on the set $\{1, 10, 100, 1000\}$ was done.
+The parameters were evaluated with stratisfied 5-fold cross-validation.
 
-The last feature feature selection method used is a RFE with Lasso.
+The last feature selection method used is Lasso logistc regression \citep{wheeler2010lasso}.
+It is a logistic regression with a $L_1$ norm as penalty for the weight vector.
+For the hyperparameter $C$ a grid search with $10$ different parameters in logarithmic scale between $10^{-5}$ and $10^3$ was done.
+The parameters were evaluated with a stratisfied 3-fold cross-validation.
 
 \begin{equation}
-  \min_w \quad \frac1{2 \, \textrm{\#features}} \, \|y - Xw\|^2_2 + \alpha \, \|w\|_1
+    \min_{w,c} \quad \|w\|_1 + C\sum_{i=1}^n \log(\exp(y_i(x_i^Tw + c))+1)
   \end{equation}
+  The advantage of this method is that we obtain a sparse weight vector as solution. This means only a small subset of features will have a significant high weight.
+  \section{Ensemble methods}
+  The different feature selection methods give as output a weight vector representing how well each feature distinguishes samples of the two classes.
+The ensemble method used aggregates the different weights vectors.
+Since different methods do not always have the same weight range, they are normalized to the range $[0,1]$.
+Moreover for the methods which can only rank data, such as methods based on RFE, their ranking are considered as weights, and so subsequently normalized the same way.
+  Those normalized weights are combined using different techniques. The methods used in this paper can be grouped in three distinct categories:
 
@@
 
-Those normalized weights are combined using different techniques. The methods used in this paper can be grouped in three distinct categories:
+Those normalized weights are combined using different techniques. The methods used in this paper can be grouped in three distinct categories
 
@@
 However, due to computation power constraints, not the whole dataset is always used.
-Additionally the colon data set (\cite{alon1999broad}) is used.
+Additionally the colon dataset (\cite{alon1999broad}) is used.
 Finally artificial data is also generated, since it is possible to control which features are meaningful.
@@
 
-The features of the artificial dataset are generated with two Gaussian distributions, depending on whether they are used in the labeling process or not.
-
+The features of the artificial dataset is generated with different Gaussian distributions, depending on whether they are used in the labeling process or not.
+It consists of $100$ significant features and $9900$ fake features.
+The significant features and fake features both consists of correlated and uncorrelated features.
+The correlation between the correlated features is randomly generated.
+The ratio of correlated features and uncorrelated features are for the significant and the fake features $0.5$.
 \begin{align}
@@
 \end{align}
+Therefore the artificial consists of $50$ correlated significant features, $50$ uncorrelated significant features, $4950$ correlated fake features and $4950$ uncorrelated fake features.
+We will call the uncorrelated features univariate features and the correlated features multivariate features in this work.
 % \text{unsignificant} \quad & f \sim 0.5 * \left[ N(0, 1) + U(-1,1) \right]
-
 To generate balanced binary labels, the significant features are first summed, then the median of the sums is subtracted, finally the sign is taken.
@@
 \subsection{Experiments}
+\label{sec:experiments}
 
@@
 
-The model performance is estimated by measuring the balanced error rate of a set of classifiers: Lasso, linear SVM, k-nearest neighbor, Random Forest.
+The model performance is estimated by measuring the balanced error rate of a set of classifiers: Lasso logistic regression, linear C-SVM, k-nearest neighbor, Random Forest. 
+%TODO describe how hyperparameters are obtained for each classifier
 For each classifier the performance was assessed using a 10-fold cross validation setting and trained on the best 1\% of the data.
@@
 
-\begin{figure}[!t]
+The experiments were perpared and executed on Python 3.4.3. For details about the libraries used see appendix \ref{apd:libraries}.
+
+\subsection{Results}
+In this section we present our results for the experiments. TODO what results
+\subsubsection{Distribution of feature selectors}
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=\textwidth]{feature_weights_hist_arcene_artificial.png}
+  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial dataset.}
+  \label{fig:feature_weights_hist_arcene_artificial}
+\end{figure}
+In figure \ref{fig:feature_weights_hist_arcene_artificial} the histograms of the features weight can be seen for the arcene and the artificial dataset.
+The histograms for all datasets can be seen in the appendix \ref{apd:plots} in figure \ref{fig:feature_weights_hist}.
+It is observable that the distribution of the feature weights have similiar shapes on each dataset for RELIEFF, SVM RFE, Lasso logistic regression.
+In addition the distributions are centered around the same area.
+RELIEFF and Lasso seem to always have a strong peak.
+Lasso even stronger than RELIEFF, which is an effect of the sparsity of Lasso.
+On the other hand SU varies a lot on different datasets and does not seem to have a consistent shape.
+For some datasets like the artifical dataset SU mainly outputs one value for all features.
+On others like arcene it is greatly distributed.
+
+\subsubsection{Results for the artificial dataset}
+\begin{figure}
+  \centering 
+  \begin{subfigure}[b]{0.48\textwidth}
+      \includegraphics[width=\textwidth]{feature_weights_plot_artificial_only_features.png}
+      \caption{Features weights for the significant features.}
+      \label{fig:feature_weights_plot_artificial_only_features}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[b]{0.48\textwidth}
+    \includegraphics[width=\textwidth]{feature_weights_plot_artificial_all.png}
+      \caption{Features weights for all features.}
+      \label{fig:feature_weights_plot_artificial_all}
+  \end{subfigure}
+
+  \caption{The features weights  once for only the significant features and once for all.
+In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the significant multivariate features and in the cyan area are the significant univariate features.
+In figure \ref{fig:feature_weights_plot_artificial_all} in the green are all significant features, in the red area are the fake multivariate features and in the orange area are the fake univariate features.
+}
+  \label{fig:feature_weights_plot_artificial}
+\end{figure}
+The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
+All feature selectors achieved similar results for the artificial dataset except of SU.
+SU does not rank iall features with a zero weight which makes SU fully random on this dataset.
+On the contrary the other feature selectors recognize parts of the inherent structure of the data.
+The univariate features are in general ranked lower than the multivariate features.
+There seems to be no diffierence in weighting between the significant und fake univariate features.
+However the significant multivariate features are ranked significantly higher than the fake multivariate features.
+As a consequence only multivariate features are selected.
+The reason why the feature selectors weight the significant univariate features this low is that the univariate features do not contribute significantly to the classification.
+If we use only the significant multivariate features with the same classification function with which the labels were created, we achieve an accuracy of $0.98$.
+On the other hand using the significant univariate features we only achieve an accuracy of $0.52$.
+Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
+Furthermore the feature seletors were evaluated after how many significant features they capture in the $100$ the highest weighted features.
+RELIEFF achieved the highest precision of $0.5$, SVM RFE achieved $0.48$, then Lasso with $0.24$ and SU with $0$.
+
+\subsubsection{Different combinations of feature selectors}
+The presented ensemble methods were used with all possible combinations of feature selectors.
+For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
+While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or not of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}.
+This is due to the low robustness of the feature selector Lasso itself.
+On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.
+
+The methods were also compared with regards to their performance and robustness on the different combinations.
+However, as can be seen in figure \ref{fig:methods_results} the methods do not seems to have a great impact on the results.
+Therefore the choice of the combined feature selectors appears to be more important than the methods used to combine them.
+
+\begin{figure}[!b]
 \centering
@@
 
-\begin{figure}[!t]
+\begin{figure}[!h]
 \centering
@@
 
-\subsection{Results}
-In this section we present our results for the experiments
-\subsubsection{Distribution of feature selectors}
-\begin{figure}[h!]
+\subsubsection{Ensemble methods in comparisment to single feature selection}
+
+To compare the different feature selection methods in relation of robustness and accuracy, the single feature selection and the three ensemble methods achieving the best results were plotted with accuracy against stability.
+For the stability the Jaccard index with $1\%$ of the features was used.
+For the accuracy the all classifiers described in \ref{sec:experiments}  reused.
+For each feature selection method the standard deviation for the accuracy and the stability on the different subsets are plotted.
+The results for the different classifiers are similar.
+In figure \ref{fig:boxplot_svm} the results for the C-SVM classifier can be observed.
+The other results can be seen in the appendix.
+%TODO boxplots for plots
+As we can see in figure \ref{fig:boxplot_svm} the ensemble methods achieve good results on each dataset.
+While single feature selection methods achieve better results in terms of accuracy and robustness on some datasets, they fail on others.
+However the ensemble methods hold their performance for each dataset.
+On the arcene dataset they even achive better results than any single feature selector.
+
+\begin{figure}[H]
   \centering
-    \includegraphics[width=\textwidth]{feature_weights_hist_arcene_artificial.png}
-  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
-  \label{fig:feature_weights_hist_arcene_artificial}
+    \includegraphics[width=\textwidth]{images/boxplot_svm.pdf}
+  \caption{The different ensemble methods compared with single feature selectors in comparisment of stability and accuracy.
+  The gray area is the accuracy when using no feature selection.}
+  \label{fig:boxplot_svm}
 \end{figure}
-In figure \ref{fig:feature_weights_hist_arcene_artificial} the histograms of the features weight can be seen for the arcene and the artificial data set.
-It is observable that the distribution of the feature weights have similiar shapes on each data set for RELIEFF, SVM RFE, Lasso logistic regression.
-In addition the distributions are centered around the same area.
-RELIEFF and Lasso seem to always have a strong peak.
-Lasso even stronger than RELIEFF, which is an effect of the sparsity of Lasso.
-On the other hand SU varies a lot on different data sets and does not seem to have a consistent shape.
-For some data sets like the artifical data set SU mainly outputs one value for all features.
-On others like arcene it is greatly distributed.
-The histograms for all data sets can be seen in the appendix in figure \ref{fig:feature_weights_hist}.
 
-\subsubsection{Results for the artificial data set}
-\begin{figure}
-  \centering 
-  \begin{subfigure}[b]{0.48\textwidth}
-      \includegraphics[width=\textwidth]{feature_weights_plot_artificial_only_features.png}
-      \caption{Features weights for the real features.}
-      \label{fig:feature_weights_plot_artificial_only_features}
-  \end{subfigure}
-  ~
-  \begin{subfigure}[b]{0.48\textwidth}
-    \includegraphics[width=\textwidth]{feature_weights_plot_artificial_all.png}
-      \caption{Features weights for all features.}
-      \label{fig:feature_weights_plot_artificial_all}
-  \end{subfigure}
-
-  \caption{The features weights for once for only the real features and once for all.
-In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the real multivariate features and in the cyan area are the real univariate features.
-In figure \ref{fig:feature_weights_plot_artificial_all} in the green are all real features, in the red area are the fake multivariate features and in the orange area are the fake univariate features.
-}
-  \label{fig:feature_weights_plot_artificial}
-\end{figure}
-\begin{figure}[h!]
-  \centering
-  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
-\end{figure}
-The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
-All feature selectors achieved similar results for the artificial data set except of SU.
-SU does not rank iall features with a zero weight which makes SU fully random on this data set.
-On the contrary the other feature selectors recognize parts of the inherent structure of the data.
-The univariate features are in general ranked lower than the multivariate features.
-There seems to be no diffierence in weighting between the real und fake univariate features.
-However the real multivariate features are ranked significantly higher than the fake multivariate features.
-As a consequence only multivariate features are selected.
-The reason why the feature selectors weight the real univariate features this low is that the univariate features do not contribute significantly to the classification.
-If we use only the real multivariate features with the same classification function with which the labels were created, we achieve an accuracy of $0.98$.
-On the other hand using the real univariate features we only achieve an accuracy of $0.52$.
-Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
-Furthermore the feature seletors were evaluated after how many real features they capture in the $100$ the highest weighted features.
-RELIEFF achieved the highest precision of $0.5$, SVM RFE achieved $0.48$, then Lasso with $0.24$ and SU with $0$.
-% Acknowledgements should go at the end, before appendices and references
-
-%\acks{I want to thank my mum}
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\subsubsection{Different combinations of feature selectors}
-The presented ensemble methods were used with all possible combinations of feature selectors.
-For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
-While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or not of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}.
-This is due to the low robustness of the feature selector Lasso itself.
-On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.
-
-The methods were also compared with regards to their performance and robustness on the different combinations.
-However, as can be seen in figure \ref{fig:methods_results} the methods do not seems to have a great impact on the results.
-Therefore the choice of the combined feature selectors appears to be more important than the methods used to combine them.
+\section{Discussion}
+We have shown that ensemble methods can hold on to results of single feauter selectors and are even superior to the tested feature selectors in terms of generality on different datasets.
+Further knowledge about the weakness and strength of certain feature selectors can exploited to create good ensembles of feature selectors.
+For the future it has to be tested if the ensemble methods in this work, will also work on oother datasets.
 
@@
 \appendix
-\section*{Appendix A.}
+\label{appendix}
+\section{Python libraries}
+\label{apd:libraries}
 For the feature selection methods SU and RELIEFF we used the scikit-feature library from \cite{Li-etal16}.
 For SVM, RFE, Lasso logistic regression we used the scikit-sklearn library from \cite{scikit-learn}
-\label{app:appendixa}
-\section*{Appendix B.}
-\label{app:appendixb}
-
+\section{Additional plots}
+\label{apd:plots}
 \begin{figure}[h!]
@@
     \includegraphics[width=\textwidth]{feature_weights_hist.png}
-  \caption{The histogram of the feature weights for all feature selectors used for all data sets used.}
+  \caption{The histogram of the feature weights for all feature selectors used for all datasets used.}
   \label{fig:feature_weights_hist}

### 2016-08-04 paper/paper.tex
typos

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{enumitem}
@@
 %TODO check if it is written that same weights are ranked random
-\author{\name Benjamin Rapier \email benjamin.rabier@campus.tu-berlin.de \\
+\author{\name Benjamin Rabier \email benjamin.rabier@campus.tu-berlin.de \\
        \addr Neural Information Processing Group\\
@@
 
-Used in Machine Learning and Statistics, ensemble methods combine multiple algorithms in order to obtain better performance.
-The bagging method, which consists of using the same algorithm on multiple subsets, has already been studied in \cite{saeys2008}.
-The method improved considerably the robustness of the feature selection algorithm while the model performance was not significantly degraded in most cases.
-The purpose of this paper is to investigate the effect of ensemble methods further by combining different feature selection methods.
+Used in machine learning and statistics, ensemble methods combine multiple algorithms in order to obtain better performance.
+The bagging method for feature selection, which consists of using the same algorithm on multiple subsets, has already been studied in \cite{saeys2008}.
+The method improved the robustness of the feature selection algorithm considerably while the model performance is not significantly degraded in most cases.
+The purpose of this paper is to extend on these results and investigate the effect of ensemble methods further by combining different feature selection methods.
 
@@
 
-Symmetrical Uncertainty (SU) \citep{press1996numerical} is entropy based measurement.
+Symmetrical Uncertainty (SU) \citep{press1996numerical} is an entropy based measurement.
 It is the normalized mutual information between the feature and the class.
 The mutual information measures the influence of the knowledge of the class on the feature value in terms of entropy and normalizes it.
-More details about mutual information can be found in \cite{paninski2003estimation}.
+It is defined as follows:
 \begin{equation}
@@
 
+More details about mutual information can be found in \cite{paninski2003estimation}.
 The second feature selection is RELIEFF \citep{kononenko1997overcoming}.
@@
 Then the difference is taken to update the weight vector representing how well each feature distinguishes samples of the two classes, as can be seen in equation \ref{eq:relief}.
-In all the experiments k was set to 5, which, empirically, gives satisfactory results.
+In all the experiments k is set to 5, which, empirically, gives satisfactory results.
 \begin{equation}
@@
 The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left.
-In the experiments, $10\%$ of the size of all features were discarded at each step.
-The procedure was repeated until a subset of the size of $1\%$ of all features was left.
+In the experiments, $10\%$ of the size of all features are discarded at each step.
+The procedure is repeated until a subset of the size of $1\%$ of all features is left.
 Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps.
@@
 Another method would be to discard only $10\%$ of the remaining features.
-A more gradually ascend of feature weights can be achievedthis way.
-However this was not computable with our ressources.
-For the hpyerparameter $C$ a grid search on the set $\{1, 10, 100, 1000\}$ was done.
-The parameters were evaluated with stratisfied 5-fold cross-validation.
+A more gradually ascend of feature weights can be achieved this way.
+However, it is not used due to the substantially increase in needed computation power.
+For the hpyerparameter $C$ a grid search on the set $\{1, 10, 100, 1000\}$ is done.
+The parameters are evaluated with stratified 5-fold cross-validation.
 
-The last feature selection method used is Lasso logistc regression \citep{wheeler2010lasso}.
+The last feature selection method used is Lasso logistic regression \citep{wheeler2010lasso}.
 It is a logistic regression with a $L_1$ norm as penalty for the weight vector.
-For the hyperparameter $C$ a grid search with $10$ different parameters in logarithmic scale between $10^{-5}$ and $10^3$ was done.
-The parameters were evaluated with a stratisfied 3-fold cross-validation.
+For the hyperparameter $C$ a grid search with $10$ different parameters in logarithmic scale between $10^{-5}$ and $10^3$ is done.
+The parameters are evaluated with a stratified 3-fold cross-validation.
 
@@
 
-Ensemble
-
 The different feature selection methods give as output a weight vector representing how well each feature distinguishes samples of the two classes.
@@
 
-Those normalized weights are combined using different techniques. The methods used in this paper can be grouped in three distinct categories
+Those normalized weights are combined using different schemes. The methods used in this paper can be grouped in two distinct categories
 
 \begin{description}[align=left]
-\item [Linear aggregation :] The average of the weights was taken as the new weight. Two version were used, one where a normalization of the weight sum is applied and the other without it.
-\item [Non-linear aggregation :] To emphasize features with importance, the weights are non-linearly transformed with the equation \ref{eq:em_non_linear}.
-$\arctan$ in in combination with $\exp$ to considerably shrink the low weights.
-Finally the weights sum is normalized.
+\item [Linear aggregation :] The average of the weights is taken as the new weight. Two version are used, one where a normalization of the weight sum is applied and the other without it.
 
-\begin{equation}
-  \label{eq:em_non_linear}
-  W_i = \frac{f \left( W_i \right)}{\sum_k f \left( W_k \right)} \quad with \quad f : x \rightarrow \exp( \arctan(x - 1) )
-\end{equation}
-
-\item [Performance related aggregation :] For each feature selector the best 1\% of the features were selected and used to measure the classification performance for multiple classifiers.
-The feature selection methods result were weighted accordingly to their accuracy.
-It was used in combination with the precedent ensemble methods.
+\item [Performance related aggregation :] For each feature selector the best 1\% of the features are selected and used to measure the classification performance for multiple classifiers.
+The results from the feature selection methods are weighted according to their accuracy.
 \end{description}
 
-Furthermore, different combinations of feature selectors were used in order to find combinations which work better than others.
+Furthermore, different combinations of feature selectors are used in order to find combinations which work better than others.
 
@@
 
-While the purpose of this paper is to find a robust feature selection method, it is also necessary to evaluate the classification performance as domain expert have no interest in badly performing model.
+While the idea of this paper is to find a robust feature selection method, it is also necessary to evaluate the classification performance.
+Domain experts usually have little interest in badly performing models.
 Hence those two aspects are always considered in combination.
@@
 Additionally the colon dataset (\cite{alon1999broad}) is used.
-Finally artificial data is also generated, since it is possible to control which features are meaningful.
+Finally, artificial data is also generated, since here it is possible to control which features are meaningful.
 
@@
     \hline
-    Name & \# Samples & \# Features & \# Class 1 & \# Class 2 & Ref\\ \hline
-    Arcene & 200 & 10 000 & 112 & 88 & \cite{NIPS} \\
-    Dexter & 600 & 20 000 & 300 & 300 & \cite{NIPS} \\
-    Gisette & 200 & 5000 & 92 & 108 & \cite{NIPS} \\
-    Colon & 62 & 2000 & 40 & 22 &  \cite{alon1999broad} \\
-    Artificial & 300 & 10 000 & 150 & 150 & \\
+    Name & \# Features & \# Samples & \# Class 1 & \# Class 2 & Ref\\ \hline
+    Arcene & 10 000 & 200 & 112 & 88 & \cite{NIPS} \\
+    Dexter & 20 000 & 600 & 300 & 300 & \cite{NIPS} \\
+    Gisette & 5000 & 200 & 92 & 108 & \cite{NIPS} \\
+    Colon & 2000 & 62 & 40 & 22 &  \cite{alon1999broad} \\
+    Artificial & 10 000 & 300 & 150 & 150 & \\
     \hline
@@
 \begin{align}
-f \sim0.5 * \left[ N(0, 1) + N(0, \Sigma) \right]  \quad \text{with} \quad \Sigma_{ij} \sim U(0,1)
+f \sim \mathcal{N}(0, 1) + \mathcal{N}(0, \Sigma)  \quad \text{with} \quad \Sigma_{ij} \sim \mathcal{U}(0,1)
 \end{align}
@@
 
-Feature selectors needs to be robust but also accurate, therefore both model performance and robustness were measured.
+Feature selectors needs to be robust but also accurate, therefore both robustness and mode performance are measured.
 
@@
 %TODO describe how hyperparameters are obtained for each classifier
-For each classifier the performance was assessed using a 10-fold cross validation setting and trained on the best 1\% of the data.
+For each classifier the performance is assessed using a 10-fold cross validation setting and trained on the best 1\% of the features.
 
-To measure the robustness, different equally sized subsamples are drawn from the dataset.
-The feature selector runs on all of them, and the best ones are taken based.
+To measure the robustness, 10 equally sized subsamples are drawn from the dataset.
+The feature selector runs on all of them, and the best ones are taken.
 The subsets are then compared with a similarity measure.
-Given that the model performance is measured on the best 1\% of the features, the order of the feature should not be of importance but only if one is or not part of the best subset.
-Hence the Jaccard Index was used because only how many features are common to both sets is important for this measure.
+Given that the model performance is measured on the best 1\% of the features, the order of the feature should not be of importance but only if one is or is not part of the best subset.
+The Jaccard Index is used because only how many features are common to both sets is important for this measure.
 For two subsets of features $F_i$ and $F_j$ it is defined as:
@@
 
-The experiments were perpared and executed on Python 3.4.3. For details about the libraries used see appendix \ref{apd:libraries}.
+The experiments are perpared and executed on Python 3.4.3. For details about the libraries used see appendix \ref{apd:libraries}.
 
 \subsection{Results}
-In this section we present our results for the experiments. TODO what results
+In this section we present our results for the experiments. %TODO what results
 \subsubsection{Distribution of feature selectors}
@@
 \end{figure}
+
 In figure \ref{fig:feature_weights_hist_arcene_artificial} the histograms of the features weight can be seen for the arcene and the artificial dataset.
 The histograms for all datasets can be seen in the appendix \ref{apd:plots} in figure \ref{fig:feature_weights_hist}.
-It is observable that the distribution of the feature weights have similiar shapes on each dataset for RELIEFF, SVM RFE, Lasso logistic regression.
+It is observable that the distribution of the feature weights have similar shapes on each dataset for RELIEFF, SVM RFE, Lasso logistic regression.
 In addition the distributions are centered around the same area.
@@
 Lasso even stronger than RELIEFF, which is an effect of the sparsity of Lasso.
-On the other hand SU varies a lot on different datasets and does not seem to have a consistent shape.
-For some datasets like the artifical dataset SU mainly outputs one value for all features.
+On the other hand SU varies a lot between the different datasets and does not seem to have a consistent shape.
+For some datasets like the artificial dataset SU mainly outputs one value for all features.
 On others like arcene it is greatly distributed.
@@
 The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
-All feature selectors achieved similar results for the artificial dataset except of SU.
-SU does not rank iall features with a zero weight which makes SU fully random on this dataset.
+All feature selectors achieved similar results for the artificial dataset except for SU.
+SU ranks all features with a zero weight, making it not better than a random feature selection on this dataset.
 On the contrary the other feature selectors recognize parts of the inherent structure of the data.
 The univariate features are in general ranked lower than the multivariate features.
-There seems to be no diffierence in weighting between the significant und fake univariate features.
+There seems to be no difference in weighting between the significant und fake univariate features.
 However the significant multivariate features are ranked significantly higher than the fake multivariate features.
@@
 The reason why the feature selectors weight the significant univariate features this low is that the univariate features do not contribute significantly to the classification.
-If we use only the significant multivariate features with the same classification function with which the labels were created, we achieve an accuracy of $0.98$.
+If we use only the significant multivariate features with the same classification function with which the labels are created, we achieve an accuracy of $0.98$.
 On the other hand using the significant univariate features we only achieve an accuracy of $0.52$.
 Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
-Furthermore the feature seletors were evaluated after how many significant features they capture in the $100$ the highest weighted features.
-RELIEFF achieved the highest precision of $0.5$, SVM RFE achieved $0.48$, then Lasso with $0.24$ and SU with $0$.
+
+Furthermore, the feature selectors are evaluated with respect to how many significant features they capture in the $100$ the highest weighted features.
+RELIEFF achieves the highest precision of $0.5$, SVM RFE achieves $0.48$, then Lasso with $0.24$ and SU with $0$.
 
 \subsubsection{Different combinations of feature selectors}
-The presented ensemble methods were used with all possible combinations of feature selectors.
-For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset.
-While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or not of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}.
+The presented ensemble methods are used with all possible combinations of feature selectors.
+For each combination, the average across subsamples  is taken, and the error bar corresponds to the mean of the variance across subsamples of each ensemble method and each dataset.
+While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or absence of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}.
 This is due to the low robustness of the feature selector Lasso itself.
@@
 
-The methods were also compared with regards to their performance and robustness on the different combinations.
-However, as can be seen in figure \ref{fig:methods_results} the methods do not seems to have a great impact on the results.
-Therefore the choice of the combined feature selectors appears to be more important than the methods used to combine them.
-
-\begin{figure}[!b]
+\begin{figure}
 \centering
@@
 
-\begin{figure}[!h]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_methods.pdf}
-  \caption{Accuracy}
-  \label{fig:methods_accuracy}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_methods.pdf}
-  \caption{Robustness}
-  \label{fig:methods_robustness}
-\end{subfigure}
-\caption{Results for the different methods on average on the different combinations.
-"Average +" is the average method with the normalized sum.
-When "\& Perf." is indicated the performance was also used to aggregate the weights.}
-\label{fig:methods_results}
-\end{figure}
+\subsubsection{Ensemble methods in comparison to single feature selection}
 
-\subsubsection{Ensemble methods in comparisment to single feature selection}
-
-To compare the different feature selection methods in relation of robustness and accuracy, the single feature selection and the three ensemble methods achieving the best results were plotted with accuracy against stability.
-For the stability the Jaccard index with $1\%$ of the features was used.
+To compare the different feature selection methods in relation of robustness and accuracy, the single feature selection and the three ensemble methods achieving the best results are plotted with accuracy against stability.
+For the stability the Jaccard index with $1\%$ of the features is used.
 For the accuracy the all classifiers described in \ref{sec:experiments}  reused.
@@
 While single feature selection methods achieve better results in terms of accuracy and robustness on some datasets, they fail on others.
-However the ensemble methods hold their performance for each dataset.
+However the ensemble methods keep their performance for each dataset.
 On the arcene dataset they even achive better results than any single feature selector.
@@
     \includegraphics[width=\textwidth]{images/boxplot_svm.pdf}
-  \caption{The different ensemble methods compared with single feature selectors in comparisment of stability and accuracy.
+  \caption{The different ensemble methods compared with single feature selectors in comparison of stability and accuracy.
   The gray area is the accuracy when using no feature selection.}
@@
 \section{Discussion}
-We have shown that ensemble methods can hold on to results of single feauter selectors and are even superior to the tested feature selectors in terms of generality on different datasets.
+We have shown that ensemble methods can keep up with results of single feature selectors and are even superior to the tested feature selectors in terms of generality over different datasets.
 Further knowledge about the weakness and strength of certain feature selectors can exploited to create good ensembles of feature selectors.
-For the future it has to be tested if the ensemble methods in this work, will also work on oother datasets.
+For the future it has to be tested if the ensemble methods in this work show similar performance on other datasets.
 

### 2016-08-05 paper/paper.tex
black and white plots added, svm -> c-svm

@@
 
-The third feature selection method used is a recursive feature elimination (RFE) with SVM \citep{guyon2002gene}.
-Recursive feature elimination fits a classifier and ranks the feature according to their importance in the model.
-In the case of the SVM, it is based on the weight vector of the hyperplane.
-More precisely after obtaining the solution for the primal problem of the SVM in equation \ref{eq:svm_primal}, the ranking coefficients $c_i$ for the features are then calculated by squaring the weights $c_i = w_i^2$.
+The third feature selection method used is a recursive feature elimination (RFE) with a C-SVM classifier \citep{guyon2002gene}. 
+The recursive feature elimination fits a classifier and ranks the feature according to their importance in the model.
+In the case of the C-SVM, it is based on the weight vector of the hyperplane.
+More precisely after obtaining the solution for the primal problem of the C-SVM in equation \ref{eq:svm_primal}, the ranking coefficients $c_i$ for the features are then calculated by squaring the weights $c_i = w_i^2$.
 \begin{alignat}{-1}
@@
 Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps.
-Therefore a SVM is $10$ times needed to be evaluated.
+Therefore a C-SVM is $10$ times needed to be evaluated.
 Another method would be to discard only $10\%$ of the remaining features.
@@
 The parameters are evaluated with stratified 5-fold cross-validation.
+In this work the RFE method with a C-SVM classifier is called SVM RFE.
 
@@
   \end{equation}
-  The advantage of this method is that we obtain a sparse weight vector as solution. This means only a small subset of features will have a significant high weight.
+  The advantage of this method is that we obtain a sparse weight vector as solution.
+This means only a small subset of features will have a significant high weight.
+In this work Lasso logistic regression is also called Lasso.
   \section{Ensemble methods}
@@
   \centering
-    \includegraphics[width=\textwidth]{feature_weights_hist_arcene_artificial.png}
+    \includegraphics[width=\textwidth]{images/feature_weights_hist_arcene_artificial.png}
   \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial dataset.}
@@
   \begin{subfigure}[b]{0.48\textwidth}
-      \includegraphics[width=\textwidth]{feature_weights_plot_artificial_only_features.png}
+      \includegraphics[width=\textwidth]{images/feature_weights_plot_artificial_only_features_bw.png}
       \caption{Features weights for the significant features.}
@@
   \begin{subfigure}[b]{0.48\textwidth}
-    \includegraphics[width=\textwidth]{feature_weights_plot_artificial_all.png}
+    \includegraphics[width=\textwidth]{images/feature_weights_plot_artificial_all_bw.png}
       \caption{Features weights for all features.}
@@
 
-  \caption{The features weights  once for only the significant features and once for all.
-In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the significant multivariate features and in the cyan area are the significant univariate features.
-In figure \ref{fig:feature_weights_plot_artificial_all} in the green are all significant features, in the red area are the fake multivariate features and in the orange area are the fake univariate features.
+  \caption{The features weights once for only the significant features and once for all features.
+In figure \ref{fig:feature_weights_plot_artificial_only_features} in the white area are the significant multivariate features and in the diagonal hatched area are the significant univariate features.
+In figure \ref{fig:feature_weights_plot_artificial_all} in the diagonal hatched area are all significant features, in the white area are the fake multivariate features and in the horizontal hatched area are the fake univariate features.
 }
@@
 This is due to the low robustness of the feature selector Lasso itself.
-On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.
+On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM RFE, are the most robust.
 
@@
 For the feature selection methods SU and RELIEFF we used the scikit-feature library from \cite{Li-etal16}.
-For SVM, RFE, Lasso logistic regression we used the scikit-sklearn library from \cite{scikit-learn}
+For C-SVM, RFE, Lasso logistic regression we used the scikit-sklearn library from \cite{scikit-learn}
 \section{Additional plots}
@@
   \centering
-    \includegraphics[width=\textwidth]{feature_weights_hist.png}
+    \includegraphics[width=\textwidth]{images/feature_weights_hist.png}
   \caption{The histogram of the feature weights for all feature selectors used for all datasets used.}
@@
 
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
+\begin{figure}[h!]
+  \centering
+    \includegraphics[width=\textwidth]{images/boxplots.pdf}
+  \caption{The different ensemble methods compared with single feature selectors in comparison of stability and accuracy.
+  The gray area is the accuracy when using no feature selection.}
+  \label{fig:boxplots}
+\end{figure}
 

### 2016-08-05 paper/paper.tex
typos

@@
 
-Feature selection is a method used in machine learning to find a small subset of features in order to build a more accurate, simpler and faster model.
+Feature selection is a method used in machine learning to find a small subset of features to build a more accurate, simpler and faster model.
 It is often used with high dimensional data.
@@
 However, in domains such as biomedical applications subsequent analysis are costly.
-Therefore not only the model performance but also the robustness of the feature selection method is important.
+Thus not only the model performance but also the robustness of the feature selection method is important.
 Domain experts would prefer a more stable algorithm to have more confidence in the selected features.
@@
 \end{equation}
+More details about mutual information can be found in \cite{paninski2003estimation}.
 
-More details about mutual information can be found in \cite{paninski2003estimation}.
 The second feature selection is RELIEFF \citep{kononenko1997overcoming}.
@@
 It is a logistic regression with a $L_1$ norm as penalty for the weight vector.
-For the hyperparameter $C$ a grid search with $10$ different parameters in logarithmic scale between $10^{-5}$ and $10^3$ is done.
+The hyperparameter $C$ is estimated with a grid search with $10$ different parameters in logarithmic scale between $10^{-5}$ and $10^3$.
 The parameters are evaluated with a stratified 3-fold cross-validation.
@@
   \end{equation}
-  The advantage of this method is that we obtain a sparse weight vector as solution.
-This means only a small subset of features will have a significant high weight.
-In this work Lasso logistic regression is also called Lasso.
-  \section{Ensemble methods}
-  The different feature selection methods give as output a weight vector representing how well each feature distinguishes samples of the two classes.
-The ensemble method used aggregates the different weights vectors.
-Since different methods do not always have the same weight range, they are normalized to the range $[0,1]$.
-Moreover for the methods which can only rank data, such as methods based on RFE, their ranking are considered as weights, and so subsequently normalized the same way.
-  Those normalized weights are combined using different techniques. The methods used in this paper can be grouped in three distinct categories:
+  The advantage of this method is to obtain a sparse weight vector as solution.
+Hence only a small subset of features have a significant high weight.
+In this work Lasso logistic regression is also called Lasso for simplicity.
 
 \section{Ensemble methods}
-
-The different feature selection methods give as output a weight vector representing how well each feature distinguishes samples of the two classes.
-Those are then be combined by the ensemble method.
+ The ensemble method used in this paper combine different feature selection methods.
+Those give as output a weight vector representing how well each feature distinguishes samples of the two classes.
+Thus the ensemble method has to aggregate the different weights vectors.
 Since different methods do not always have the same weight range, they are normalized to the range $[0,1]$.
@@
 
-Those normalized weights are combined using different schemes. The methods used in this paper can be grouped in two distinct categories
+ The normalized weights are combined using different techniques. The ones used in this paper can be grouped in two distinct categories:
 
@@
 Therefore the artificial consists of $50$ correlated significant features, $50$ uncorrelated significant features, $4950$ correlated fake features and $4950$ uncorrelated fake features.
-We will call the uncorrelated features univariate features and the correlated features multivariate features in this work.
-% \text{unsignificant} \quad & f \sim 0.5 * \left[ N(0, 1) + U(-1,1) \right]
-To generate balanced binary labels, the significant features are first summed, then the median of the sums is subtracted, finally the sign is taken.
+In this work, the uncorrelated features and the correlated features are also respectively called univariate and  multivariate features.
+To generate balanced binary labels the significant features are first summed, then the median of the sum is subtracted, finally the sign is taken.
 
@@
 Given that the model performance is measured on the best 1\% of the features, the order of the feature should not be of importance but only if one is or is not part of the best subset.
-The Jaccard Index is used because only how many features are common to both sets is important for this measure.
+The Jaccard Index is used because only how many features are common to both sets is important.
 For two subsets of features $F_i$ and $F_j$ it is defined as:
@@
 \subsection{Results}
-In this section we present our results for the experiments. %TODO what results
+In this section the results of the different experiments are presented.
+First the distribution of the weights given by the feature selectors is analyzed.
+Secondly the results on the artificial dataset is discussed.
+Then the influence of different combination of feature selectors is analyzed.
+Finally the a comparison between the ensemble methods and the feature selectors is made.
+
 \subsubsection{Distribution of feature selectors}
@@
 The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
-All feature selectors achieved similar results for the artificial dataset except for SU.
+All feature selectors achieve similar results for the artificial dataset except for SU.
 SU ranks all features with a zero weight, making it not better than a random feature selection on this dataset.
@@
 The reason why the feature selectors weight the significant univariate features this low is that the univariate features do not contribute significantly to the classification.
-If we use only the significant multivariate features with the same classification function with which the labels are created, we achieve an accuracy of $0.98$.
-On the other hand using the significant univariate features we only achieve an accuracy of $0.52$.
+If only the significant multivariate features are used with classification function used to generate the labels, an accuracy of $0.98$ is obtained.
+On the other hand using only the significant univariate features the accuracy drops to $0.52$.
 Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
@@
 %TODO boxplots for plots
-As we can see in figure \ref{fig:boxplot_svm} the ensemble methods achieve good results on each dataset.
+As can be seen in figure \ref{fig:boxplot_svm} the ensemble methods achieve good results on each dataset.
 While single feature selection methods achieve better results in terms of accuracy and robustness on some datasets, they fail on others.
 However the ensemble methods keep their performance for each dataset.
-On the arcene dataset they even achive better results than any single feature selector.
+On the arcene dataset they even achieve better results than any single feature selector.
 
@@
 \section{Discussion}
-We have shown that ensemble methods can keep up with results of single feature selectors and are even superior to the tested feature selectors in terms of generality over different datasets.
-Further knowledge about the weakness and strength of certain feature selectors can exploited to create good ensembles of feature selectors.
+This work shows that ensemble methods can keep up with results of single feature selectors and are even superior to the tested feature selectors in terms of generality over different datasets.
+Further knowledge about the weakness and strength of certain feature selectors can exploited to create good combinations of feature selectors.
 For the future it has to be tested if the ensemble methods in this work show similar performance on other datasets.
@@
 \label{apd:libraries}
-For the feature selection methods SU and RELIEFF we used the scikit-feature library from \cite{Li-etal16}.
-For C-SVM, RFE, Lasso logistic regression we used the scikit-sklearn library from \cite{scikit-learn}
+For the feature selection methods SU and RELIEFF come from the scikit-feature library (\cite{Li-etal16}).
+For C-SVM, RFE, Lasso logistic regression come from the scikit-sklearn library (\cite{scikit-learn}).
 \section{Additional plots}

### 2016-08-05 paper/paper.tex
typos

@@
 Finally, artificial data is also generated, since here it is possible to control which features are meaningful.
+The datasets and the number of samples used are indicated in table \ref{table:datasets}.
 
@@
     \end{tabular}
+  \label{table:datasets}
+  \captionof{table}{Datasets used in the experiments}
 \end{center}
@@
 The ratio of correlated features and uncorrelated features are for the significant and the fake features $0.5$.
-\begin{align}
-f \sim \mathcal{N}(0, 1) + \mathcal{N}(0, \Sigma)  \quad \text{with} \quad \Sigma_{ij} \sim \mathcal{U}(0,1)
-\end{align}
+\begin{alignat}{-1}
+\text{uncorrelated features} & \sim & \mathcal{N}(0, 1) & \\ 
+\text{correlated features} & \sim & \mathcal{N}(0, \Sigma) & \quad \text{with} \quad \Sigma_{ij} \sim \mathcal{U}(0,1)
+\end{alignat}
 Therefore the artificial consists of $50$ correlated significant features, $50$ uncorrelated significant features, $4950$ correlated fake features and $4950$ uncorrelated fake features.

### 2016-08-05 paper/paper.tex
small changes

--- 2016-08-05 paper/paper.tex
@@
 The second feature selection is RELIEFF \citep{kononenko1997overcoming}.
-For each sample $x_i$ the k nearest neighboring samples, using the $L_1$ norm, belonging the same class $\{\textrm{Near-hit}_{i, j}\}_{j=1..k}$ and the ones of the opposite class $\{\textrm{Near-miss}_{i, j}\}_{j=1..k}$ are selected.
+For each sample $x_i$ the k nearest neighboring samples, using the $L_1$ norm as metric, belonging to the same class $\{\textrm{Near-hit}_{i, j}\}_{j=1..k}$ and the ones of the opposite class $\{\textrm{Near-miss}_{i, j}\}_{j=1..k}$ are selected.
 Then the difference is taken to update the weight vector representing how well each feature distinguishes samples of the two classes, as can be seen in equation \ref{eq:relief}.
-In all the experiments k is set to 5, which, empirically, gives satisfactory results.
+In all the experiments k is set to 5, which empirically gives satisfactory results.
 \begin{equation}
@@
 \end{equation}
-
-The third feature selection method used is a recursive feature elimination (RFE) with a C-SVM classifier \citep{guyon2002gene}. 
-The recursive feature elimination fits a classifier and ranks the feature according to their importance in the model.
+The third feature selection method uses recursive feature elimination (RFE) with a linear C-SVM classifier \citep{guyon2002gene} to weight the features. 
+The RFE method fits a classifier and ranks the feature according to their importance in the model.
 In the case of the C-SVM, it is based on the weight vector of the hyperplane.
@@
 \end{alignat}
-
 The worst ranked features are then discarded and the procedure is repeated until only a subset of features is left.
@@
 The procedure is repeated until a subset of the size of $1\%$ of all features is left.
-Since each step $10\%$ of the features are discarded, the overall process takes $10$ steps.
-Therefore a C-SVM is $10$ times needed to be evaluated.
+Since in each step $10\%$ of all features are discarded, the overall process takes $10$ steps.
+Therefore a C-SVM is needed to be $10$ times evaluated.
 Another method would be to discard only $10\%$ of the remaining features.
@@
 The parameters are evaluated with stratified 5-fold cross-validation.
-In this work the RFE method with a C-SVM classifier is called SVM RFE.
+In this work the RFE method with a C-SVM classifier is abbreviated as SVM RFE.
 
@@
 The parameters are evaluated with a stratified 3-fold cross-validation.
-
 \begin{equation}
@@
 Hence only a small subset of features have a significant high weight.
-In this work Lasso logistic regression is also called Lasso for simplicity.
+In this work Lasso logistic regression is also abbreviated as Lasso for simplicity.
 
@@
 \begin{description}[align=left]
-\item [Linear aggregation :] The average of the weights is taken as the new weight. Two version are used, one where a normalization of the weight sum is applied and the other without it.
+\item [Linear aggregation :] The average of the weights is taken as the new weight. Two version are used, one where a normalization of the weight sum is applied and one without this normalization.
 
@@
 Finally, artificial data is also generated, since here it is possible to control which features are meaningful.
+All data sets are binary labelled.
 
@@
 In this section the results of the different experiments are presented.
-First the distribution of the weights given by the feature selectors is analyzed.
-Secondly the results on the artificial dataset is discussed.
-Then the influence of different combination of feature selectors is analyzed.
-Finally the a comparison between the ensemble methods and the feature selectors is made.
+Firstly, the distribution of the weights given by the feature selectors is analyzed.
+Secondly, the results on the artificial dataset is discussed.
+Afterwards the influence of different combinations of feature selectors is analyzed.
+Finally, a comparison between the ensemble methods and the feature selectors is made.
 

### 2016-08-05 paper/paper.tex

@@
 \section{Feature selection methods}
-
+\label{sec:fs_methods}
 Symmetrical Uncertainty (SU) \citep{press1996numerical} is an entropy based measurement.
@@
 The parameters are evaluated with stratified 5-fold cross-validation.
-In this work the RFE method with a C-SVM classifier is abbreviated as SVM RFE.
+In this work the RFE method with a C-SVM classifier is abbreviated as SVM RFE and sometimes SVM when it should be clear from the context.
 
@@
 Finally, artificial data is also generated, since here it is possible to control which features are meaningful.
+The datasets and the number of samples used are indicated in table \ref{table:datasets}.
 All data sets are binary labelled.
@@
 The model performance is estimated by measuring the balanced error rate of a set of classifiers: Lasso logistic regression, linear C-SVM, k-nearest neighbor, Random Forest.
-%TODO describe how hyperparameters are obtained for each classifier
-For each classifier the performance is assessed using a 10-fold cross validation setting and trained on the best 1\% of the features.
+The hyperparameter for Lasso logistic regression and linear C-SVM are obtained in the same way as for the feature selection in section \ref{sec:fs_methods}.
+For k-nearest neighbor 3 neighbor were used.
+For Random Forest we used 1 tree with a maximal depth of 5.
+For each classifier the performance is assessed using a 10-fold cross validation setting and trained on the best $1\%$ of the features.
 
@@
 The feature selector runs on all of them, and the best ones are taken.
-The subsets are then compared with a similarity measure.
-Given that the model performance is measured on the best 1\% of the features, the order of the feature should not be of importance but only if one is or is not part of the best subset.
-The Jaccard Index is used because only how many features are common to both sets is important.
+The subsets are then pairwise over all combinations compared with a similarity measure.
+Given that the model performance is measured on the best 1\% of the features, the order of the features should not be of importance but only if one feature is or is not part of the best subset.
+To measure the similarity between two subsets of features, the amount of features, which are in both subsets, is only important.
+Therefore we use the Jaccard Index as robustness measurement.
 For two subsets of features $F_i$ and $F_j$ it is defined as:
@@
 
-Furthermore, the feature selectors are evaluated with respect to how many significant features they capture in the $100$ the highest weighted features.
+Furthermore, the feature selectors are evaluated with respect to how many significant features they capture in the $100$ highest weighted features.
 RELIEFF achieves the highest precision of $0.5$, SVM RFE achieves $0.48$, then Lasso with $0.24$ and SU with $0$.
@@
 For the stability the Jaccard index with $1\%$ of the features is used.
-For the accuracy the all classifiers described in \ref{sec:experiments}  reused.
+For the accuracy the all classifiers described in \ref{sec:experiments} are reused.
 For each feature selection method the standard deviation for the accuracy and the stability on the different subsets are plotted.
@@
 In figure \ref{fig:boxplot_svm} the results for the C-SVM classifier can be observed.
-The other results can be seen in the appendix.
-%TODO boxplots for plots
+The other results can be seen in the appendix \ref{apd:plots} in figure \ref{fig:boxplots}.
 As can be seen in figure \ref{fig:boxplot_svm} the ensemble methods achieve good results on each dataset.
@@
 On the arcene dataset they even achieve better results than any single feature selector.
+On the artificial dataset all classifiers achieve bette results with feature selection than without.
+For the other datasets the C-SVM classifier without feature selection achieve better results except of colon where similar results are achieved.
+Furthermore the random feature selection method does also achieve good results in terms of accuracy on the datasets colon, arcene and gisette.
 
@@
   \caption{The different ensemble methods compared with single feature selectors in comparison of stability and accuracy.
-  The gray area is the accuracy when using no feature selection.}
+  The gray area is the accuracy when using all features.}
   \label{fig:boxplot_svm}
@@
 \label{apd:libraries}
-For the feature selection methods SU and RELIEFF come from the scikit-feature library (\cite{Li-etal16}).
-For C-SVM, RFE, Lasso logistic regression come from the scikit-sklearn library (\cite{scikit-learn}).
+For the feature selection methods SU and RELIEFF the scikit-feature library \citep{Li-etal16} is used.
+For C-SVM, RFE, Lasso logistic regression the scikit-sklearn library \citep{scikit-learn} is used.
 \section{Additional plots}
